### 2020-03-07 paper/paper.tex
added dataset

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Spectral-Spatial Hyper-spectral Image Classification Using Dual-Channel Capsule Networks}
\author{liu wenbo}
\date{March 2020}

\begin{document}

\maketitle
\section{ABSTRACT}
\section{INTRODUCTION}
\section{RELATED WORKS}
\subsection{Capsule Network}
\subsection{Margin Loss}
\section{PROPOSED METHOD}
\subsection{Network Architecture}
\section{EXPERIMENT}
\section{DISCUSSION}
\section{CONCLUSION}
\section{REFERENCE}

\end{document}

### 2020-03-08 paper/paper.tex
added dataset

@@
 	\maketitle
-\section{ABSTRACT}
-\section{INTRODUCTION}
-\section{RELATED WORKS}
-\subsection{Capsule Network}
-\subsection{Margin Loss}
-\section{PROPOSED METHOD}
-\subsection{Network Architecture}
-\section{EXPERIMENT}
-\section{DISCUSSION}
-\section{CONCLUSION}
-\section{REFERENCE}
+
+	\section{ABSTRACT}\label{sec:abstract}
+	Deep learning methods have shown their marvel performance on hyper-spectral image (HSI) classification tasks.
+	In particular,algorithms based on Convolution Neural Network (CNN) outperforms most of the conventional machine-
+	learning based algorithms.
+	Recently, a newly proposed neural network called Capsule Network (CapsNet) showed its potential to replace the CNNs
+	in various classification tasks with its amazing performance.
+	In this paper, we proposed a new CapsNet architecture for HSI classification tasks, called Dual-channel Capsule
+	Network (DCCN).
+	Our DCCN model extracts features from spectral and special domain respectively with two separate convolution
+	channels and then concatenates and feds the features into the capsule layer to classify each of the HSI pixels.
+	The model is trained on \textbf{2/3/4/5?} real HSI dataset \textbf{Pavia University, Pavia City, Salinas Valley,
+	Salinas A and KSC} and achieved high accuracy.
+	We also compared our network with some of the state-of-art models and found our model was superior to those models.
+
+	\section{INTRODUCTION}\label{sec:introduction}
+
+	\section{RELATED WORKS}\label{sec:related-works}
+
+	\subsection{Capsule Network}\label{subsec:capsule-network}
+
+	\subsection{Margin Loss}\label{subsec:margin-loss}
+
+	\section{PROPOSED METHOD}\label{sec:proposed-method}
+
+	\subsection{Network Architecture}\label{subsec:network-architecture}
+
+	\subsection{Data Pre-Process}\label{subsec:data-pre-process}
+
+	\subsection{Training the Network}\label{subsec:training-the-network}
+
+	\section{EXPERIMENT}\label{sec:experiment}
+
+	\subsection{Dataset Introduction}\label{subsec:dataset-introduction}
+
+	\subsection{Environment}\label{subsec:environment}
+
+	\subsection{Result and Analysis}\label{subsec:result-and-analysis}
+
+	\section{DISCUSSION}\label{sec:discussion}
+
+	\subsection{Convergence analysis}\label{subsec:convergence}
+
+	\section{CONCLUSION}\label{sec:conclusion}
 

### 2020-03-08 utils.py

@@ -88,7 +88,7 @@ def calMixMatrix(probMap, groundTruth):
 def selectData(DATA=1):
 	if DATA == 1:
 		pathName = []
-		pathName.append("./data/Indian_pines.mat")
+		pathName.append("./data/Indian_pines_corrected.mat")
 		pathName.append("./data/Indian_pines_gt.mat")
 		matName = []
 		matName.append("indian_pines")

### 2020-03-08 paper/paper.tex
fixed some bugs

@@
 \usepackage[utf8]{inputenc}
+\usepackage{fullpage}
 
@@
 	in various classification tasks with its amazing performance.
-	In this paper, we proposed a new CapsNet architecture for HSI classification tasks, called Dual-channel Capsule
-	Network (DCCN).
+	In this paper, we proposed a new network architecture based on CapsNet for HSI classification tasks, called
+	Dual-channel Capsule Network (DCCN).
 	Our DCCN model extracts features from spectral and special domain respectively with two separate convolution
 	channels and then concatenates and feds the features into the capsule layer to classify each of the HSI pixels.
-	The model is trained on \textbf{2/3/4/5?} real HSI dataset \textbf{Pavia University, Pavia City, Salinas Valley,
-	Salinas A and KSC} and achieved high accuracy.
+	The model is trained and tested on \textbf{(2/3/4/5?)} real HSI dataset \textbf{(Pavia University, Pavia City,
+	Salinas Valley, Salinas A and KSC)} and achieved high accuracy.
 	We also compared our network with some of the state-of-art models and found our model was superior to those models.
+
+	\textbf{Key words:} Dual-Channel Capsule Network, Hyper-Spectral Image, Image Classification.
 

### 2020-03-08 seeData.py

@@ -4,16 +4,16 @@ import matplotlib.pyplot as plt
 import matplotlib as mpl
 import os
 
-# dic=scio.loadmat("data/Salinas_corrected.mat")["salinas_corrected"]
+dic=scio.loadmat("data/Indian_pines_corrected.mat")
 # dic=scio.loadmat("data/SalinasA_corrected.mat")["salinasA_corrected"]
 # dic = scio.loadmat("data/Botswana.mat")["Botswana"]
-dicc = scio.loadmat("data/Botswana_gt.mat")["Botswana_gt"]
-dic = ["black", "snow", "red", "tomato", "chocolate", "orange", "wheat", "gold", "yellow", "chartreuse",
-	   "limegreen", "aquamarine", "cyan", "dodgerblue", "slateblue", "violet", "pink"]
-cmap = mpl.colors.ListedColormap(dic[0:len(np.unique(dicc))])
-plt.imshow(dicc,cmap=cmap)
-sv = plt.gcf()
-sv.savefig(os.path.join(".", "gt.png"), format="png", dpi=300)
-plt.show()
+# dicc = scio.loadmat("data/Botswana_gt.mat")["Botswana_gt"]
+# dic = ["black", "snow", "red", "tomato", "chocolate", "orange", "wheat", "gold", "yellow", "chartreuse",
+# 	   "limegreen", "aquamarine", "cyan", "dodgerblue", "slateblue", "violet", "pink"]
+# cmap = mpl.colors.ListedColormap(dic[0:len(np.unique(dicc))])
+# plt.imshow(dicc,cmap=cmap)
+# sv = plt.gcf()
+# sv.savefig(os.path.join(".", "gt.png"), format="png", dpi=300)
+# plt.show()
 
-print(np.unique(dicc))
+print(dic)

### 2020-03-08 utils.py

@@ -88,10 +88,10 @@ def calMixMatrix(probMap, groundTruth):
 def selectData(DATA=1):
 	if DATA == 1:
 		pathName = []
-		pathName.append("./data/Indian_pines_corrected.mat")
+		pathName.append("./data/indian_pines_corrected.mat")
 		pathName.append("./data/Indian_pines_gt.mat")
 		matName = []
-		matName.append("indian_pines")
+		matName.append("indian_pines_corrected")
 		matName.append("indian_pines_gt")
 		print("using indian pines**************************")
 	elif DATA == 2:

### 2020-03-08 utils.py
fixed some bugs

@@ -88,7 +88,7 @@ def calMixMatrix(probMap, groundTruth):
 def selectData(DATA=1):
 	if DATA == 1:
 		pathName = []
-		pathName.append("./data/indian_pines_corrected.mat")
+		pathName.append("./data/Indian_pines_corrected.mat")
 		pathName.append("./data/Indian_pines_gt.mat")
 		matName = []
 		matName.append("indian_pines_corrected")

### 2020-03-08 paper/paper.tex
fixed some bugs

@@
 	Salinas Valley, Salinas A and KSC)} and achieved high accuracy.
-	We also compared our network with some of the state-of-art models and found our model was superior to those models.
+	We also compared our network with some of the state-of-art models and found our model outperformed these models.
+	Among these state-of-art models we also implemented the Capsule Network that has the same architecture as our
+	network except the spectral convolution channel, and we found the DCCN model was superior to it as well.
 
-	\textbf{Key words:} Dual-Channel Capsule Network, Hyper-Spectral Image, Image Classification.
+	\noindent \textbf{Key Words:} Dual-Channel Capsule Network, Hyper-Spectral Image, Image Classification.
 
@@
 
-	\section{RELATED WORKS}\label{sec:related-works}
+	The remainder of the paper is organized as follows.
+	In section~\ref{sec:related-works}, we introduce some related work of our paper.
+	In section~\ref{sec:proposed-method}, we describe the structure of our proposed network, how we pre-process the data and how
+	to train the network.
+	In section~\ref{sec:experiment}, we present and analyze the result of out experiment.
+	In section~\ref{sec:discussion}, we further explore the potential of DCCN\@.
+	Finally, in section~\ref{sec:conclusion}, we  conclude this paper with some remarks and hints at plausible future research
+	lines.
+
+	\section{RELATED WORK}\label{sec:related-works}
 

### 2020-03-09 train.py
fixed some bugs

@@ -20,6 +20,7 @@ parser.add_argument("-p", "--patch_size", default=9, type=int)
 parser.add_argument("-m", "--model", default=1, type=int)
 parser.add_argument("-d", "--directory", default="./save/default")
 parser.add_argument("--model_path", default="./save/default/model")
+parser.add_argument("--sum_path",default="./save/default/sum")
 parser.add_argument("--drop", default=1, type=float)
 parser.add_argument("--data", default=0, type=int)
 parser.add_argument("--first_layer", default=6, type=int)
@@ -50,6 +51,7 @@ DONT_SAVE_DATA = args.dont_save_data
 NO_DETAILED_SUMMARY=args.no_detailed_summary
 DRAW = args.draw
 FIRST_LAYER, SECOND_LAYER = args.first_layer, args.second_layer
+SUM_PATH=args.sum_path
 
 os.environ["CUDA_VISIBLE_DEVICES"] = args.gpu
 if not os.path.exists(DIRECTORY):
@@ -57,9 +59,13 @@ if not os.path.exists(DIRECTORY):
 	os.makedirs(os.path.join(DIRECTORY, "data"))
 if not os.path.exists(MODEL_DIRECTORY):
 	os.makedirs(MODEL_DIRECTORY)
+if not os.path.exists(SUM_PATH):
+	os.makedirs(SUM_PATH)
+
 modelSavePath = os.path.join(MODEL_DIRECTORY, "model.ckpt")
 imgSavePath = os.path.join(DIRECTORY, "img")
 dataSavePath = os.path.join(DIRECTORY, "data")
+sumSavePath=SUM_PATH
 
 pathName, matName = selectData(DATA)
 dataloader = DataLoader(pathName, matName, PATCH_SIZE, RATIO, AUGMENT_RATIO)
@@ -174,10 +180,15 @@ with tf.Session() as sess:
 			trainProcess.save()
 		probMap.save()
 
+
 	OA = calOA(probMap.map, allLabeledLabel)
 	AA = calAA(probMap.map, allLabeledLabel)
 	kappa = calKappa(probMap.map, allLabeledLabel)
 	mixMatrix = calMixMatrix(probMap.map, allLabeledLabel)
+
+	with open(os.path.join(sumSavePath, "sum.txt"), "a+") as f:
+		print("data:%d, oa: %4f, aa:%4f, kappa:%4f" % \
+		      (DATA, OA, AA, kappa), file=f)
[…]

### 2020-03-09 scripts/3090.sh
fixed some bugs

@@ -1,38 +1,30 @@
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-3090/ --model_path ./save/mar4-3090/ --data 6 --first_layer 6 --second_layer 14 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-3090/ --model_path ./save/mar4-3090/ --data 6 --first_layer 6 --second_layer 16 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-3090/ --model_path ./save/mar4-3090/ --data 6 --first_layer 8 --second_layer 6 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-3090/ --model_path ./save/mar4-3090/ --data 6 --first_layer 8 --second_layer 8 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-3090/ --model_path ./save/mar4-3090/ --data 6 --first_layer 8 --second_layer 10 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-3090/ --model_path ./save/mar4-3090/ --data 6 --first_layer 8 --second_layer 12 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-3090/ --model_path ./save/mar4-3090/ --data 6 --first_layer 8 --second_layer 14 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-3090/ --model_path ./save/mar4-3090/ --data 6 --first_layer 8 --second_layer 16 --dont_save_data --no_detailed_summary
[…]

### 2020-03-09 scripts/3091.sh

@@ -1,38 +1,30 @@
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3091/ --model_path ./save/mar4-3091/ --data 2 --first_layer 12 --second_layer 6 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3091/ --model_path ./save/mar4-3091/ --data 2 --first_layer 12 --second_layer 8 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3091/ --model_path ./save/mar4-3091/ --data 2 --first_layer 12 --second_layer 10 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3091/ --model_path ./save/mar4-3091/ --data 2 --first_layer 12 --second_layer 12 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3091/ --model_path ./save/mar4-3091/ --data 2 --first_layer 12 --second_layer 14 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3091/ --model_path ./save/mar4-3091/ --data 2 --first_layer 12 --second_layer 16 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3091/ --model_path ./save/mar4-3091/ --data 4 --first_layer 6 --second_layer 6 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3091/ --model_path ./save/mar4-3091/ --data 4 --first_layer 6 --second_layer 8 --dont_save_data --no_detailed_summary
[…]

### 2020-03-09 scripts/3092.sh

@@ -1,38 +1,30 @@
-python ./train.py -e 50 -b 50 -l 0.0001 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3092/ --model_path ./save/mar4-3092/ --data 5 --first_layer 8 --second_layer 10 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3092/ --model_path ./save/mar4-3092/ --data 5 --first_layer 8 --second_layer 12 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3092/ --model_path ./save/mar4-3092/ --data 5 --first_layer 8 --second_layer 14 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3092/ --model_path ./save/mar4-3092/ --data 5 --first_layer 8 --second_layer 16 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3092/ --model_path ./save/mar4-3092/ --data 5 --first_layer 10 --second_layer 6 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3092/ --model_path ./save/mar4-3092/ --data 5 --first_layer 10 --second_layer 8 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3092/ --model_path ./save/mar4-3092/ --data 5 --first_layer 10 --second_layer 10 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3092/ --model_path ./save/mar4-3092/ --data 5 --first_layer 10 --second_layer 12 --dont_save_data --no_detailed_summary
[…]

### 2020-03-09 scripts/3093.sh

@@ -1,38 +1,30 @@
-python ./train.py -e 50 -b 50 -l 0.0001 -g 3 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3093/ --model_path ./save/mar4-3093/ --data 6 --first_layer 12 --second_layer 14 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 3 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-3093/ --model_path ./save/mar4-3093/ --data 6 --first_layer 12 --second_layer 16 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 3 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-3093/ --model_path ./save/mar4-3093/ --data 2 --first_layer 6 --second_layer 6 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 3 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-3093/ --model_path ./save/mar4-3093/ --data 2 --first_layer 6 --second_layer 8 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 3 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-3093/ --model_path ./save/mar4-3093/ --data 2 --first_layer 6 --second_layer 10 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 3 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-3093/ --model_path ./save/mar4-3093/ --data 2 --first_layer 6 --second_layer 12 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 3 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-3093/ --model_path ./save/mar4-3093/ --data 2 --first_layer 6 --second_layer 14 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 3 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-3093/ --model_path ./save/mar4-3093/ --data 2 --first_layer 6 --second_layer 16 --dont_save_data --no_detailed_summary
[…]

### 2020-03-09 scripts/3090.sh
fixed some bugs

@@ -1,30 +1,30 @@
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p5\pu\1\ --model_path .\save\formal0307\model\DCCN\p5\pu\1\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p5\pu\sum --draw
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p5\pu\2\ --model_path .\save\formal0307\model\DCCN\p5\pu\2\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p5\pu\sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p5\pu\3\ --model_path .\save\formal0307\model\DCCN\p5\pu\3\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p5\pu\sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p5\pu\4\ --model_path .\save\formal0307\model\DCCN\p5\pu\4\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p5\pu\sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p5\pu\5\ --model_path .\save\formal0307\model\DCCN\p5\pu\5\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p5\pu\sum --dont_save_data
[…]

### 2020-03-09 scripts/3091.sh

@@ -1,30 +1,30 @@
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p7\pu\1\ --model_path .\save\formal0307\model\DCCN\p7\pu\1\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p7\pu\sum --draw
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p7\pu\2\ --model_path .\save\formal0307\model\DCCN\p7\pu\2\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p7\pu\sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p7\pu\3\ --model_path .\save\formal0307\model\DCCN\p7\pu\3\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p7\pu\sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p7\pu\4\ --model_path .\save\formal0307\model\DCCN\p7\pu\4\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p7\pu\sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p7\pu\5\ --model_path .\save\formal0307\model\DCCN\p7\pu\5\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p7\pu\sum --dont_save_data
[…]

### 2020-03-09 scripts/3092.sh

@@ -1,30 +1,30 @@
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p9\pu\1\ --model_path .\save\formal0307\model\DCCN\p9\pu\1\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p9\pu\sum --draw
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p9\pu\2\ --model_path .\save\formal0307\model\DCCN\p9\pu\2\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p9\pu\sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p9\pu\3\ --model_path .\save\formal0307\model\DCCN\p9\pu\3\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p9\pu\sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p9\pu\4\ --model_path .\save\formal0307\model\DCCN\p9\pu\4\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p9\pu\sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d .\save\formal0307\data\DCCN\p9\pu\5\ --model_path .\save\formal0307\model\DCCN\p9\pu\5\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0307\model\DCCN\p9\pu\sum --dont_save_data
[…]

### 2020-03-09 scripts/3093.sh

@@ -1,30 +1,30 @@
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d .\save\formal0309\data\DCCN\p11\pu\1\ --model_path .\save\formal0309\model\DCCN\p11\pu\1\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0309\model\DCCN\p11\pu\sum --draw
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d .\save\formal0309\data\DCCN\p11\pu\2\ --model_path .\save\formal0309\model\DCCN\p11\pu\2\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0309\model\DCCN\p11\pu\sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d .\save\formal0309\data\DCCN\p11\pu\3\ --model_path .\save\formal0309\model\DCCN\p11\pu\3\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0309\model\DCCN\p11\pu\sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d .\save\formal0309\data\DCCN\p11\pu\4\ --model_path .\save\formal0309\model\DCCN\p11\pu\4\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0309\model\DCCN\p11\pu\sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d .\save\formal0309\data\DCCN\p11\pu\5\ --model_path .\save\formal0309\model\DCCN\p11\pu\5\ --first_layer 8 --second_layer 16 --use_best_model --sum_path .\save\formal0309\model\DCCN\p11\pu\sum --dont_save_data
[…]

### 2020-03-09 scripts/3090.sh
fixed some bugs

@@ -1,30 +1,30 @@
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p5/pu/1/ --model_path ./save/formal0307/model/DCCN/p5/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p5/pu/sum --draw
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p5/pu/2/ --model_path ./save/formal0307/model/DCCN/p5/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p5/pu/3/ --model_path ./save/formal0307/model/DCCN/p5/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p5/pu/4/ --model_path ./save/formal0307/model/DCCN/p5/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p5/pu/5/ --model_path ./save/formal0307/model/DCCN/p5/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p5/pu/sum --dont_save_data
[…]

### 2020-03-09 scripts/3091.sh

@@ -1,30 +1,30 @@
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p7/pu/1/ --model_path ./save/formal0307/model/DCCN/p7/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p7/pu/sum --draw
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p7/pu/2/ --model_path ./save/formal0307/model/DCCN/p7/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p7/pu/3/ --model_path ./save/formal0307/model/DCCN/p7/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p7/pu/4/ --model_path ./save/formal0307/model/DCCN/p7/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p7/pu/5/ --model_path ./save/formal0307/model/DCCN/p7/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p7/pu/sum --dont_save_data
[…]

### 2020-03-09 scripts/3092.sh

@@ -1,30 +1,30 @@
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p9/pu/1/ --model_path ./save/formal0307/model/DCCN/p9/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p9/pu/sum --draw
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p9/pu/2/ --model_path ./save/formal0307/model/DCCN/p9/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p9/pu/3/ --model_path ./save/formal0307/model/DCCN/p9/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p9/pu/4/ --model_path ./save/formal0307/model/DCCN/p9/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0307/data/DCCN/p9/pu/5/ --model_path ./save/formal0307/model/DCCN/p9/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0307/model/DCCN/p9/pu/sum --dont_save_data
[…]

### 2020-03-09 paper/paper.tex
fixed some bugs
write some paper

@@
 \usepackage{fullpage}
+\usepackage{graphicx}
 
@@
 \begin{document}
+	\bibliographystyle{IEEEtran}
 
@@
 	Dual-channel Capsule Network (DCCN).
-	Our DCCN model extracts features from spectral and special domain respectively with two separate convolution
+	Our DCCN model extracts features from spectral and spatial domain respectively with two separate convolution
 	channels and then concatenates and feds the features into the capsule layer to classify each of the HSI pixels.
@@
 	\section{INTRODUCTION}\label{sec:introduction}
+	With technology developing, high resolution hyper-spectral images (HSI) became readily available.
+	Containing hundreds of spectral bands, HSI becomes a ideal method to further explore the earth's
+	surface\cite{du2013foreword,bioucas2013hyperspectral,shippert2003introduction}.
+	With a wealth of information, HSI has been applied in various fields, e.g.,
+	land cover classification\cite{yan2015urban},
+	object detection\cite{eslami2015developing},
+	forest inventory\cite{matsuki2015hyperspectral}
+	and water source management\cite{govender2007review}.
+	Therefore, HSI classification has become a quite significant problem to solve.
+	It aims at assigning a specific label to each pixel according to its spectral-spatial information\cite{wang2018scene}.
 
@@
 	In section~\ref{sec:related-works}, we introduce some related work of our paper.
-	In section~\ref{sec:proposed-method}, we describe the structure of our proposed network, how we pre-process the data and how
-	to train the network.
+	In section~\ref{sec:proposed-method}, we describe the structure of our proposed network, how we pre-process the data
+	and how to train the network.
 	In section~\ref{sec:experiment}, we present and analyze the result of out experiment.
 	In section~\ref{sec:discussion}, we further explore the potential of DCCN\@.
-	Finally, in section~\ref{sec:conclusion}, we  conclude this paper with some remarks and hints at plausible future research
-	lines.
+	Finally, in section~\ref{sec:conclusion}, we conclude this paper with some remarks and hints at plausible future
+	research lines.
 
@@
 
-	\subsection{Network Architecture}\label{subsec:network-architecture}
+	In this section, we introduce our proposed algorithm.
+	We first described how we pre-process the HSI data, then we \textbf{depicted} the network structure and finally we
+	introduced how to train the network.
 
@@
 
-	\subsection{Training the Network}\label{subsec:training-the-network}
+	\subsection{Network Architecture}\label{subsec:network-architecture}
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[width=0.4\textwidth]{pic/lossAndAcc.eps}
+		\caption{Proposed network architecture.}
+		\label{netArct}
+	\end{figure}
+	Our proposed network architecture is showed in~\ref{netArct}.
+	As is shown, our Dual-Channel Capsule Network contains two convolution channel, i.e., a 2D convolution channel to
+	process the patch and a 1D convolution channel to process the spectrum, and a capsule channel.
+	As we can see, the Dual-Channel Capsule Network we adopted is a very shallow network, containing only six layers,
+	that is, a convolution layer append with a activation layer and a primary capsule layer in both of the spectral
+	channel and the spatial channel, two capsule layer in the fully connected capsule channel and a output layer to
+	process the output from the latter capsule layer.
+
+	To be specific, the detailed parameter of the DCCN deployed in our experiment are as follows.
+	For the spatial channel, the first layer is a 2D convolution layer, including 50 filters with the kernel size of
+	3$*$3 and stride of 1.
+	The following activation layer uses ReLU function as activation function.
+	The primary capsule layer uses 64 filters with kernel size of 3$*$3 and stride of 1.
+	Its output capsule's dimension is 8.
+	For the spectral channel, the first layer is a 1D convolution layer,including 30 filters with kernel size of 32 and
+	stride of 8.
+	The following activation layer used ReLU activation function as well.
+	The primary capsule layer uses 64 filters with kernel size of 3 and stride of 1.
+	Its output capsule's dimension is 8 so that it can be concatenated with the spatial channel's output capsules and
+	then fed into the fully connected capsule layer.
+%	TODO: the following 3 layer.
+
+	And here's how the data flows in the DCCN.
+	First, the sliced patch is fed into the 2D convolution channel to extract features spatially, and the spectrum
+	of the patch's center pixel is fed into the 1D convolution channel to extract features in spectral domain in
+	parallel.
+	Then, the extracted features, both spectral and spatial, are concatenated and fed into the capsule channel to output
+	the vectors (that is, the capsule) whose module represents the probability of a pixel being assigned a specific
+	label.
+	After that, the output layer will squash the 2D tensor (made up by capsules) into a 1D vector (Let's call it the
+	probability vector(prob-vector in short), since each of its elements represents the probability of a pixel should be
+	assigned to the according class) by calculating each of the capsule's module.
+	And finally, the output layer will assign a label to the pixel by performing argument-max ($argmax$) function to the
+	prob-vector.
+
+	\subsection{Train the Network}\label{subsec:train-the-network}
 
@@
 
+	\bibliography{cite}
 \end{document}

### 2020-03-09 postProcess.py

@@ -70,7 +70,7 @@ class TrainProcess:
         sv.savefig(os.path.join(self.imgDir, "lossAndAcc.eps"), format="eps", dpi=300)
 
     def drawLoss(self):
-        plt.figure()
+        plt.figure(figsize=(8, 4.5))
         x = range(len(self.trainLoss))
         plt.title("Loss of training and testing")
         plt.plot(x, self.trainLoss, label="train loss")
@@ -80,7 +80,7 @@ class TrainProcess:
         sv.savefig(os.path.join(self.imgDir, "loss.eps"), format="eps", dpi=300)
 
     def drawAcc(self):
-        plt.figure()
+        plt.figure(figsize=(8, 4.5))
         x = range(len(self.trainAcc))
         plt.title("accuracy of training and testing")
         plt.plot(x, self.trainAcc, label="train loss")

### 2020-03-10 paper/paper.tex
write some paper
added color map

@@
 	For the spatial channel, the first layer is a 2D convolution layer, including 50 filters with the kernel size of
-	3$*$3 and stride of 1.
+	3×3 and stride of 1.
 	The following activation layer uses ReLU function as activation function.
-	The primary capsule layer uses 64 filters with kernel size of 3$*$3 and stride of 1.
-	Its output capsule's dimension is 8.
+	The primary capsule layer uses 64 filters with kernel size of 3×3 and stride of 1.
+	Its output capsules' dimension is 8.
 	For the spectral channel, the first layer is a 1D convolution layer,including 30 filters with kernel size of 32 and
@@
 	The primary capsule layer uses 64 filters with kernel size of 3 and stride of 1.
-	Its output capsule's dimension is 8 so that it can be concatenated with the spatial channel's output capsules and
+	Its output capsules' dimension is 8 so that it can be concatenated with the spatial channel's output capsules and
 	then fed into the fully connected capsule layer.
-%	TODO: the following 3 layer.
+	For the first capsule layer, it has \textbf{100 or so?} capsules, which each contains 8 neurons inside.
+	The second capsule layer has $n_{classes}$ capsules with 16 neurons inside, where $n_{classes}$ denotes how many
+	different classes of pixels inside the HSI dataset.
+	So far, the main part of the DCCN model has finished.
+	But as is mentioned before, the method we proposed is end-to-end, so we added a output layer to process the output
+	of the network.
+	The output layer will squash the 2D tensor ,made up by capsules, into a 1D vector (Let's call the 1D vector
+	probability vector ,prob-vector in short, since each of its elements represents the probability of a pixel should
+	be assigned to the according class.) by replacing each of the capsule with its module and perform argument-max
+	($argmax$) function to gain the pixel's label.
 
@@
 	label.
-	After that, the output layer will squash the 2D tensor (made up by capsules) into a 1D vector (Let's call it the
-	probability vector(prob-vector in short), since each of its elements represents the probability of a pixel should be
-	assigned to the according class) by calculating each of the capsule's module.
-	And finally, the output layer will assign a label to the pixel by performing argument-max ($argmax$) function to the
-	prob-vector.
+	And finally, the output layer will squash the outputted 2D tensor and assign a label to the pixel by performing
+	$argmax$ function to the prob-vector.
 

### 2020-03-10 postProcess.py

@@ -7,262 +7,291 @@ from tqdm import tqdm
 from mpl_toolkits.mplot3d import Axes3D
 import matplotlib as mpl
 from utils import TQDM_ASCII
+import seaborn as sns
 
 
 class TrainProcess:
-    def __init__(self, path):
-        self.trainLoss = np.array([])
-        self.trainAcc = np.array([])
-        self.testLoss = np.array([])
-        self.testAcc = np.array([])
-        self.dataDir = os.path.join(path, "data")
-        self.imgDir = os.path.join(path, "img")
-        if not os.path.exists(self.imgDir):
-            os.makedirs(self.imgDir)
+	def __init__(self, path):
+		self.trainLoss = np.array([])
+		self.trainAcc = np.array([])
+		self.testLoss = np.array([])
+		self.testAcc = np.array([])
+		self.dataDir = os.path.join(path, "data")
+		self.imgDir = os.path.join(path, "img")
+		if not os.path.exists(self.imgDir):
+			os.makedirs(self.imgDir)
 
-    def addData(self, trainLoss, trainAcc, testLoss, testAcc):
-        self.trainLoss = np.append(self.trainLoss, trainLoss)
-        self.trainAcc = np.append(self.trainAcc, trainAcc)
-        self.testLoss = np.append(self.testLoss, testLoss)
-        self.testAcc = np.append(self.testAcc, testAcc)
+	def addData(self, trainLoss, trainAcc, testLoss, testAcc):
+		self.trainLoss = np.append(self.trainLoss, trainLoss)
+		self.trainAcc = np.append(self.trainAcc, trainAcc)
+		self.testLoss = np.append(self.testLoss, testLoss)
+		self.testAcc = np.append(self.testAcc, testAcc)
 
-    def save(self):
-        f = open(os.path.join(self.dataDir, "trainLoss.pkl"), "wb")
-        pickle.dump(self.trainLoss, f)
-        f = open(os.path.join(self.dataDir, "trainAcc.pkl"), "wb")
-        pickle.dump(self.trainAcc, f)
-        f = open(os.path.join(self.dataDir, "testLoss.pkl"), "wb")
-        pickle.dump(self.testLoss, f)
-        f = open(os.path.join(self.dataDir, "testAcc.pkl"), "wb")
-        pickle.dump(self.testAcc, f)
+	def save(self):
+		f = open(os.path.join(self.dataDir, "trainLoss.pkl"), "wb")
[…]

### 2020-03-10 seeData.py

@@ -3,8 +3,9 @@ import numpy as np
 import matplotlib.pyplot as plt
 import matplotlib as mpl
 import os
+import seaborn as sns
 
-dic=scio.loadmat("data/Indian_pines_corrected.mat")
+dic=scio.loadmat("data/Indian_pines_gt.mat")["indian_pines_gt"]
 # dic=scio.loadmat("data/SalinasA_corrected.mat")["salinasA_corrected"]
 # dic = scio.loadmat("data/Botswana.mat")["Botswana"]
 # dicc = scio.loadmat("data/Botswana_gt.mat")["Botswana_gt"]
@@ -15,5 +16,20 @@ dic=scio.loadmat("data/Indian_pines_corrected.mat")
 # sv = plt.gcf()
 # sv.savefig(os.path.join(".", "gt.png"), format="png", dpi=300)
 # plt.show()
-
-print(dic)
+palette = {0: (0, 0, 0)}
+for k, color in enumerate(sns.color_palette("hls", len(np.unique(dic))-1)):
+	palette[k + 1] = tuple(np.asarray(255 * np.array(color), dtype='uint8'))
+# print(palette)
+for i in palette:
+	print(palette[i])
+# plt.show()
+def convertToColor(palette,map):
+	a=np.zeros(shape=(np.shape(map)[0],np.shape(map)[1],3),dtype=np.uint8)
+	for i in range(np.shape(map)[0]):
+		for j in range(np.shape(map)[1]):
+			a[i][j]=palette[map[i][j]]
+	return a
+if __name__=="__main__":
+	a=convertToColor(palette,dic)
+	plt.imshow(a)
+	plt.show()

### 2020-03-10 paper/paper.tex
added color map

@@
 	\subsection{Data Pre-Process}\label{subsec:data-pre-process}
+	The original HSI dataset is usually a chunk of 3D tensor that is too large to feed into the neural network, so we
+	have to do some process before input it into the DCCN\@.
+	On one hand, we extracted the pixel with its neighbour pixels' spectrum and grouped them as a spectral cube, namely
+	a patch.
+	On the other, we extracted the single pixel's spectrum as a 1D vector.
+	The pixel's spectrum vector will be combined with its corresponding patch to feed into the DCCN model simultaneously.
+	The patch an be assigned with different size.
+	In our experiment, we set it as 7×7×$n_{bands}$.
+
+	Usually, a HSI dataset has labeled and unlabeled pixels.
+	In our experiment we discarded those unlabeled pixels, only using the labeled pixels for training and testing.
+	We divided the labeled pixels into 3 groups in our experiment: training data, testing data and validating data.
+	We randomly selected 10\% of the total labeled pixels as training set, then we randomly selected 100 labeled pixels
+	and the rest of the labeled pixels was used to validate the model.
 
@@
 	\subsection{Train the Network}\label{subsec:train-the-network}
+	At first, we randomly shuffled the training set and divided it into several batches.
+	These batches ,instead of single pixel, would be feed into the model for training to accelerate the training process.
+	In our experiment, considering the training speed and final accuracy, we set the batch size as 50.
 

### 2020-03-10 paper/paper.tex
wrote some paper

@@
 	These batches ,instead of single pixel, would be feed into the model for training to accelerate the training process.
-	In our experiment, considering the training speed and final accuracy, we set the batch size as 50.
+	In our experiment, considering the training speed and final accuracy, we set the batch size to 50.
+	As for the loss function, we adopted the margin loss mentioned in section~\ref{sec:related-works}, instead of the
+	usually used cross-entropy loss function.
+	The network is trained using a first-order gradient-based optimization of stochastic objection, referred to as the
+	Adam algorithm.
+	Therefore, our training goal is to minimize the margin loss using the Adam optimizer, and we set the learning rate
+	to 0.0001.
+	When all batches have been fed into the network and finished training, we say the training process finished an epoch.
+	In our experiment, we conducted 100 epochs for each of the dataset.
 
 	\section{EXPERIMENT}\label{sec:experiment}
+	In this section, we showed and analyzed the training result.
+	We compared our model with six neural network based algorithms i.e., 1D CNN\cite{hu2015deep},
+	2D CNN\cite{sharma2016hyperspectral},
+	3D CNN\cite{hamida20183},
+	3D FCN\cite{lee2016contextual},
+	CNN-MRF\cite{cao2018hyperspectral},
+	the CapsNet that is identical to our DCCN model except the spectral channel and the machine learning algorithm SVM\@.
+	The accuracy metrics we used includes overall accuracy(OA), average accuracy(AA) and Kappa Coefficient($\kappa$).
 
 	\subsection{Dataset Introduction}\label{subsec:dataset-introduction}
+	In our experiment, we selected 4 real HSI dataset to train and test our DCCN model separately, that is, the
+	Pavia University dataset, the Pavia Center dataset, the Salinas Valley dataset and the Salinas A dataset, which is
+	a small subset of the Salinas Valley dataset.
+	The first three of them are relatively large dataset and the last one is relatively small.
+	We use these 4 dataset to test the robustness of out model when performing on different scale dataset.
+	Here follows the brief introduction of the four dataset.
 
 	\subsection{Environment}\label{subsec:environment}
+	We trained and tested the model on a PC with 4 NVIDIA RTX 2080Ti(11GB) GPUs, dual Xeon 4210 Processor
+	and 128GB of memory.
+	The operating system is Ubuntu server 18.04 x64 LTS\@.
+	We implement the model with Tensorflow 1.14.0 and the model is trained and tested on GPU\@.
 

### 2020-03-11 paper/paper.tex
wrote some paper

@@
 \usepackage{graphicx}
+\usepackage{enumerate}
 
@@
 	Here follows the brief introduction of the four dataset.
+	\begin{enumerate}[1)]
+		\item \textit{Pavia Center and University} These are two scenes acquired by the ROSIS sensor during a flight
+		campaign over Pavia, northern Italy.
+		The number of spectral bands is 102 for Pavia Centre and 103 for Pavia University.
+		Pavia Centre is a 1096*1096 pixels image, and Pavia University is 610*610 pixels, but some of the samples in
+		both images contain no information and have to be discarded before the analysis, so the final picture size is
+		1096*715 and 610*340.
+		The geometric resolution is 1.3 meters.
+		Both image has 9 different ground truth classes each.
+		\item \textit{Salinas Scene} The Salinas scene was collected by the 224-band AVIRIS sensor over Salinas Valley,
+		California, and is characterized by high spatial resolution (3.7-meter pixels).
+		The Salinas Valley dataset is a 512*217 pixels image, and the Salinas A is a subset of the Salinas Valley
+		containing 86*83 pixels.
+		The Salinas scene dataset has been discarded 20 water absorption bands from the original image, so there's 204
+		bands left in both of the tow dataset.
+		The Salinas Valley dataset has 16 different classes but the Salinas A only has 6 different classes.
+	\end{enumerate}
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[width=0.25\textwidth]{pic/pavia_gt.eps}
+		\includegraphics[width=0.25\textwidth]{pic/paviaU_gt.eps}
+		\includegraphics[width=0.25\textwidth]{pic/salinas_gt.eps}
+		\includegraphics[width=0.25\textwidth]{pic/salinasA_gt.eps}
+		\caption{The dataset we used}
+		\label{gt}
+	\end{figure}
+
+	\begin{table}[h]
+		\centering
+		\begin{tabular}{@{}lll|l@{}}
+			\toprule
+			\textit{Weather}    & \textit{Food} & \textit{Meeting}  & \textit{Attend?} \\ \midrule
+			cold                & full          & idc               & yes              \\
+			cold & empty & no & no               \\
+			hot & full & yes & yes              \\
+			cold & full & no & yes              \\
+			hot & empty & no & no               \\ \bottomrule
+		\end{tabular}
+		\caption{Dataset $\D$\label{table:1}}
+	\end{table}
+	\crule[blue]{1cm}{1cm}
+	\crule[#123456]{1cm}{1cm}
 

### 2020-03-11 scripts/3090.sh

@@ -1,30 +1,30 @@
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p5/pu/1/ --model_path ./save/formal0309/model/DCCN/p5/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p5/pu/sum --draw
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p5/pu/2/ --model_path ./save/formal0309/model/DCCN/p5/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p5/pu/3/ --model_path ./save/formal0309/model/DCCN/p5/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p5/pu/4/ --model_path ./save/formal0309/model/DCCN/p5/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p5/pu/5/ --model_path ./save/formal0309/model/DCCN/p5/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p5/pu/sum --dont_save_data
[…]

### 2020-03-11 seeData.py

@@ -1,35 +1,40 @@
 import scipy.io as scio
 import numpy as np
 import matplotlib.pyplot as plt
-import matplotlib as mpl
-import os
 import seaborn as sns
+from utils import selectData
+import os
 
-dic=scio.loadmat("data/Indian_pines_gt.mat")["indian_pines_gt"]
-# dic=scio.loadmat("data/SalinasA_corrected.mat")["salinasA_corrected"]
-# dic = scio.loadmat("data/Botswana.mat")["Botswana"]
-# dicc = scio.loadmat("data/Botswana_gt.mat")["Botswana_gt"]
-# dic = ["black", "snow", "red", "tomato", "chocolate", "orange", "wheat", "gold", "yellow", "chartreuse",
-# 	   "limegreen", "aquamarine", "cyan", "dodgerblue", "slateblue", "violet", "pink"]
-# cmap = mpl.colors.ListedColormap(dic[0:len(np.unique(dicc))])
-# plt.imshow(dicc,cmap=cmap)
-# sv = plt.gcf()
-# sv.savefig(os.path.join(".", "gt.png"), format="png", dpi=300)
-# plt.show()
-palette = {0: (0, 0, 0)}
-for k, color in enumerate(sns.color_palette("hls", len(np.unique(dic))-1)):
-	palette[k + 1] = tuple(np.asarray(255 * np.array(color), dtype='uint8'))
+
+# dic=scio.loadmat("data/Indian_pines_gt.mat")["indian_pines_gt"]
 # print(palette)
-for i in palette:
-	print(palette[i])
+# for i in palette:
+# 	print(palette[i])
 # plt.show()
-def convertToColor(palette,map):
-	a=np.zeros(shape=(np.shape(map)[0],np.shape(map)[1],3),dtype=np.uint8)
+def convertToColor(palette, map):
+	a = np.zeros(shape=(np.shape(map)[0], np.shape(map)[1], 3), dtype=np.uint8)
 	for i in range(np.shape(map)[0]):
 		for j in range(np.shape(map)[1]):
-			a[i][j]=palette[map[i][j]]
+			a[i][j] = palette[map[i][j]]
 	return a
-if __name__=="__main__":
-	a=convertToColor(palette,dic)
-	plt.imshow(a)
-	plt.show()
+
+
+if __name__ == "__main__":
+	for i in range(7):
+		path, mat = selectData(i)
[…]

### 2020-03-11 paper/paper.tex
wrote some paper

--- 2020-03-10 paper/paper.tex
@@
 \usepackage{graphicx}
+\usepackage{enumerate}
+\usepackage{xcolor}
 
@@
 \date{March 2020}
+
+\newcommand\crule[3][black]{\textcolor{#1}{\rule{#2}{#3}}}
+%color map definition
+%pavia c
+\definecolor{paviaU0}{RGB}{0, 0, 0}
+\definecolor{paviaU1}{RGB}{219, 94, 86}
+\definecolor{paviaU2}{RGB}{219, 183, 86}
+\definecolor{paviaU3}{RGB}{167, 219, 86}
+\definecolor{paviaU4}{RGB}{86, 219, 94}
+\definecolor{paviaU5}{RGB}{86, 219, 183}
+\definecolor{paviaU6}{RGB}{86, 167, 219}
+\definecolor{paviaU7}{RGB}{94, 86, 219}
+\definecolor{paviaU8}{RGB}{183, 86, 219}
+\definecolor{paviaU9}{RGB}{219, 86, 167}
+%pavia c
+\definecolor{pavia0}{RGB}{0, 0, 0}
+\definecolor{pavia1}{RGB}{219, 94, 86}
+\definecolor{pavia2}{RGB}{219, 183, 86}
+\definecolor{pavia3}{RGB}{167, 219, 86}
+\definecolor{pavia4}{RGB}{86, 219, 94}
+\definecolor{pavia5}{RGB}{86, 219, 183}
+\definecolor{pavia6}{RGB}{86, 167, 219}
+\definecolor{pavia7}{RGB}{94, 86, 219}
+\definecolor{pavia8}{RGB}{183, 86, 219}
+\definecolor{pavia9}{RGB}{219, 86, 167}
+%salinas
+\definecolor{salinas_corrected0}{RGB}{0, 0, 0}
+\definecolor{salinas_corrected1}{RGB}{219, 94, 86}
+\definecolor{salinas_corrected2}{RGB}{219, 144, 86}
+\definecolor{salinas_corrected3}{RGB}{219, 194, 86}
+\definecolor{salinas_corrected4}{RGB}{194, 219, 86}
+\definecolor{salinas_corrected5}{RGB}{145, 219, 86}
+\definecolor{salinas_corrected6}{RGB}{95, 219, 86}
+\definecolor{salinas_corrected7}{RGB}{86, 219, 127}
+\definecolor{salinas_corrected8}{RGB}{86, 219, 177}
+\definecolor{salinas_corrected9}{RGB}{86, 211, 219}
+\definecolor{salinas_corrected10}{RGB}{86, 161, 219}
+\definecolor{salinas_corrected11}{RGB}{86, 111, 219}
+\definecolor{salinas_corrected12}{RGB}{111, 86, 219}
+\definecolor{salinas_corrected13}{RGB}{160, 86, 219}
+\definecolor{salinas_corrected14}{RGB}{210, 86, 219}
+\definecolor{salinas_corrected15}{RGB}{219, 86, 178}
+\definecolor{salinas_corrected16}{RGB}{219, 86, 128}
+%salinas a
+\definecolor{salinasA_corrected0}{RGB}{0, 0, 0}
+\definecolor{salinasA_corrected1}{RGB}{219, 94, 86}
+\definecolor{salinasA_corrected2}{RGB}{211, 219, 86}
+\definecolor{salinasA_corrected3}{RGB}{86, 219, 94}
+\definecolor{salinasA_corrected4}{RGB}{86, 211, 219}
+\definecolor{salinasA_corrected5}{RGB}{94, 86, 219}
+\definecolor{salinasA_corrected6}{RGB}{219, 86, 211}
 
@@
 	Here follows the brief introduction of the four dataset.
+	\begin{enumerate}[1)]
+		\item \textit{Pavia Center and University} These are two scenes acquired by the ROSIS sensor during a flight
+		campaign over Pavia, northern Italy.
+		The number of spectral bands is 102 for Pavia Centre and 103 for Pavia University.
+		Pavia Centre is a 1096*1096 pixels image, and Pavia University is 610*610 pixels, but some of the samples in
+		both images contain no information and have to be discarded before the analysis, so the final picture size is
+		1096*715 and 610*340.
+		The geometric resolution is 1.3 meters.
+		Both image has 9 different ground truth classes each(see table\ref{paviagt}).
+		\begin{table}[h]
+			\centering
+			\begin{tabular}{|c|c|}
+				\hline
+				\textbf{PAVIA CENTER}    & \textbf{PAVIA UNIVERSITY}\\
+				\hline
+				\includegraphics[width=0.4\textwidth]{pic/pavia_gt.eps}&
+				\includegraphics[width=0.4\textwidth]{pic/paviaU_gt.eps}\\
+				\hline
+				\begin{tabular}{ccc}
+					\footnotesize
+					\textit{color}&\textit{land-cover type}&\textit{number}\\
+					\hline
+					\crule[pavia1]{0.02\textwidth}{0.02\textwidth} &Water &824    \\
+					\crule[pavia2]{0.02\textwidth}{0.02\textwidth} &Trees &820    \\
+					\crule[pavia3]{0.02\textwidth}{0.02\textwidth} &Asphalt &816    \\
+					\crule[pavia4]{0.02\textwidth}{0.02\textwidth} &Self-Blocking Bricks &808    \\
+					\crule[pavia5]{0.02\textwidth}{0.02\textwidth} &Bitumen &808    \\
+					\crule[pavia6]{0.02\textwidth}{0.02\textwidth} &Tiles &1260   \\
+					\crule[pavia7]{0.02\textwidth}{0.02\textwidth} &Shadows &476    \\
+					\crule[pavia8]{0.02\textwidth}{0.02\textwidth} &Meadows &824    \\
+					\crule[pavia9]{0.02\textwidth}{0.02\textwidth} &Bare Soil &820    \\
+				\end{tabular}&
+				\begin{tabular}{ccc}
+					\footnotesize
+					\textit{color}&\textit{land-cover type}&\textit{number}\\
+					\hline
+					\crule[paviaU1]{0.02\textwidth}{0.02\textwidth} &Asphalt &6631   \\
+					\crule[paviaU2]{0.02\textwidth}{0.02\textwidth} &Meadows &18649  \\
+					\crule[paviaU3]{0.02\textwidth}{0.02\textwidth} &Gravel &2099   \\
+					\crule[paviaU4]{0.02\textwidth}{0.02\textwidth} &Trees &3064   \\
+					\crule[paviaU5]{0.02\textwidth}{0.02\textwidth} &Painted metal sheets &1345   \\
+					\crule[paviaU6]{0.02\textwidth}{0.02\textwidth} &Bare Soil &5029   \\
+					\crule[paviaU7]{0.02\textwidth}{0.02\textwidth} &Bitumen &1330   \\
+					\crule[paviaU8]{0.02\textwidth}{0.02\textwidth} &Self-Blocking Bricks &3682   \\
+					\crule[paviaU9]{0.02\textwidth}{0.02\textwidth} &Shadows &947    \\
+				\end{tabular}\\
+				\hline
+			\end{tabular}
+			\caption{Number of samples in two Pavia scene dataset.}
+			\label{paviagt}
+		\end{table}
+		\item \textit{Salinas Scene} The Salinas scene was collected by the 224-band AVIRIS sensor over Salinas Valley,
+		California, and is characterized by high spatial resolution (3.7-meter pixels).
+		The Salinas Valley dataset is a 512*217 pixels image, and the Salinas A is a subset of the Salinas Valley
+		containing 86*83 pixels.
+		The Salinas scene dataset has been discarded 20 water absorption bands from the original image, so there's 204
+		bands left in both of the tow dataset.
+		The Salinas Valley dataset has 16 different classes but the Salinas A only has 6 different classes(see
+		table\ref{salinas_gt}).
+		\begin{table}[h]
+			\centering
+			\begin{tabular}{|c|c|}
+				\hline
+				\textbf{SALINAS VALLEY}  & \textbf{SALINAS A}\\
+				\hline
+				\includegraphics[width=0.4\textwidth]{pic/salinas_gt.eps}&
+				\includegraphics[width=0.4\textwidth]{pic/salinasA_gt.eps}\\
+				\hline
+				\begin{tabular}{ccc}
+					\footnotesize
+					\textit{color}&\textit{land-cover type}&\textit{number}\\
+					\hline
+					\crule[salinas_corrected1]{0.02\textwidth}{0.02\textwidth} &Brocoli green weeds-1 &2009  \\
+					\crule[salinas_corrected2]{0.02\textwidth}{0.02\textwidth} &Brocoli green weeds-2 &3726  \\
+					\crule[salinas_corrected3]{0.02\textwidth}{0.02\textwidth} &Fallow &1976  \\
+					\crule[salinas_corrected4]{0.02\textwidth}{0.02\textwidth} &Fallow rough plow &1394  \\
+					\crule[salinas_corrected5]{0.02\textwidth}{0.02\textwidth} &Fallow smooth &2678  \\
+					\crule[salinas_corrected6]{0.02\textwidth}{0.02\textwidth} &Stubble &3959  \\
+					\crule[salinas_corrected7]{0.02\textwidth}{0.02\textwidth} &Celery &3579  \\
+					\crule[salinas_corrected8]{0.02\textwidth}{0.02\textwidth} &Grapes untrained &11271  \\
+					\crule[salinas_corrected9]{0.02\textwidth}{0.02\textwidth} &Soil vinyard develop &6203  \\
+					\crule[salinas_corrected10]{0.02\textwidth}{0.02\textwidth} &Corn senesced green weeds &3278  \\
+					\crule[salinas_corrected11]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-4wk &1068  \\
+					\crule[salinas_corrected12]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-5wk &1927  \\
+					\crule[salinas_corrected13]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-6wk &916  \\
+					\crule[salinas_corrected14]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-7wk &1070  \\
+					\crule[salinas_corrected15]{0.02\textwidth}{0.02\textwidth} &Vinyard untrained &7268  \\
+					\crule[salinas_corrected16]{0.02\textwidth}{0.02\textwidth} &Vinyard vertical trellis &1807  \\
+				\end{tabular}&
+				\begin{tabular}{ccc}
+					\footnotesize
+					\textit{color}&\textit{land-cover type}&\textit{number}\\
+					\hline
+					\crule[salinasA_corrected1]{0.02\textwidth}{0.02\textwidth} &Brocoli green weeds-1 &391  \\
+					\crule[salinasA_corrected2]{0.02\textwidth}{0.02\textwidth} &Corn senesced green weeds &1343  \\
+					\crule[salinasA_corrected3]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-4wk &616  \\
+					\crule[salinasA_corrected4]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-5wk &1525  \\
+					\crule[salinasA_corrected5]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-6wk &674  \\
+					\crule[salinasA_corrected6]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-7wk &799  \\
+					\\
+					\\
+					\\
+					\\
+					\\
+					\\
+					\\
+					\\
+					\\
+					\\
+				\end{tabular}\\
+				\hline
+			\end{tabular}
+			\caption{Number of samples in the two Salinas scene dataset.}
+			\label{salinas_gt}
+		\end{table}
+	\end{enumerate}
 

### 2020-03-11 scripts/3091.sh

@@ -1,30 +1,30 @@
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p7/pu/1/ --model_path ./save/formal0309/model/DCCN/p7/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p7/pu/sum --draw
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p7/pu/2/ --model_path ./save/formal0309/model/DCCN/p7/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p7/pu/3/ --model_path ./save/formal0309/model/DCCN/p7/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p7/pu/4/ --model_path ./save/formal0309/model/DCCN/p7/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p7/pu/5/ --model_path ./save/formal0309/model/DCCN/p7/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p7/pu/sum --dont_save_data
[…]

### 2020-03-11 scripts/3092.sh

@@ -1,30 +1,30 @@
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p9/pu/1/ --model_path ./save/formal0309/model/DCCN/p9/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p9/pu/sum --draw
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p9/pu/2/ --model_path ./save/formal0309/model/DCCN/p9/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p9/pu/3/ --model_path ./save/formal0309/model/DCCN/p9/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p9/pu/4/ --model_path ./save/formal0309/model/DCCN/p9/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p9/pu/5/ --model_path ./save/formal0309/model/DCCN/p9/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p9/pu/sum --dont_save_data
[…]

### 2020-03-11 scripts/3093.sh

@@ -1,30 +1,30 @@
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p11/pu/1/ --model_path ./save/formal0309/model/DCCN/p11/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p11/pu/sum --draw
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p11/pu/2/ --model_path ./save/formal0309/model/DCCN/p11/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p11/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p11/pu/3/ --model_path ./save/formal0309/model/DCCN/p11/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p11/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p11/pu/4/ --model_path ./save/formal0309/model/DCCN/p11/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p11/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0309/data/DCCN/p11/pu/5/ --model_path ./save/formal0309/model/DCCN/p11/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0309/model/DCCN/p11/pu/sum --dont_save_data
[…]

### 2020-03-11 seeData.py

@@ -20,12 +20,9 @@ def convertToColor(palette, map):
 
 
 if __name__ == "__main__":
-	for i in range(7):
+	for i in (2,3,4,5):
 		path, mat = selectData(i)
 		dic = scio.loadmat(path[1])[mat[1]]
-		print(mat[1], np.shape(dic))
-		continue
-
 		unique = np.unique(dic)
 		lut = np.zeros(np.max(unique) + 1, dtype=np.int)
 		for iter, i in enumerate(unique):
@@ -34,7 +31,9 @@ if __name__ == "__main__":
 		palette = {0: (0, 0, 0)}
 		for k, color in enumerate(sns.color_palette("hls", len(np.unique(dic)) - 1)):
 			palette[k + 1] = tuple(np.asarray(255 * np.array(color), dtype='uint8'))
-		gt = convertToColor(palette, dic)
-		plt.imshow(gt)
-		sv = plt.gcf()
-		sv.savefig(".\\paper\\pic\\" + mat[1] + ".eps", format="eps", dpi=300)
+		for i in palette:
+			print("\definecolor{%s%d}{RGB}{%d, %d, %d}"%(mat[0],i,palette[i][0],palette[i][1],palette[i][2]))
+		# gt = convertToColor(palette, dic)
+		# plt.imshow(gt)
+		# sv = plt.gcf()
+		# sv.savefig(".\\paper\\pic\\" + mat[1] + ".eps", format="eps", dpi=300)

### 2020-03-11 paper/paper.tex
fixed some bugs

@@
 \usepackage{xcolor}
+\usepackage{subfiles}
 
@@
 	In this section, we introduce our proposed algorithm.
-	We first described how we pre-process the HSI data, then we \textbf{depicted} the network structure and finally we
-	introduced how to train the network.
+	We first described how we pre-process the HSI data, then we introduced the network structure and finally we
+	introduced the hyper parameters we adopted to train the network.
 
@@
 	In our experiment, we set it as 7×7×$n_{bands}$.
-
-	Usually, a HSI dataset has labeled and unlabeled pixels.
-	In our experiment we discarded those unlabeled pixels, only using the labeled pixels for training and testing.
-	We divided the labeled pixels into 3 groups in our experiment: training data, testing data and validating data.
-	We randomly selected 10\% of the total labeled pixels as training set, then we randomly selected 100 labeled pixels
-	and the rest of the labeled pixels was used to validate the model.
 
@@
 	\end{enumerate}
+	Usually, a HSI dataset has labeled and unlabeled pixels.
+	In our experiment we discarded those unlabeled pixels, only using the labeled pixels for training and testing.
+	We divided the labeled pixels into 3 groups in our experiment: training data, testing data and validating data.
+	We randomly selected 10\% of the total labeled pixels as training set, then we randomly selected 100 labeled pixels
+	and the rest of the labeled pixels was used to validate the model.
+	The training and validating dataset are shown in figure~\ref{trainMaps} and figure~\ref{testMaps}
+
+	\begin{figure}
+		\begin{subfigure}
+			\includegraphics{pic/p5/pc/1/img/trainMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}
+			\includegraphics{pic/p5/pu/1/img/trainMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}
+			\includegraphics{pic/p5/sl/1/img/trainMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}
+			\includegraphics{pic/p5/sa/1/img/trainMap.eps}
+			\caption{}
+		\end{subfigure}
+		\caption{Training set for (a) Pavia Center, (b) Pavia University, (c) Salinas Valley and (d) Salinas A}
+		\label{trainMaps}
+	\end{figure}
+
+	\begin{figure}
+		\begin{subfigure}
+			\includegraphics{pic/p5/pc/1/img/testMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}
+			\includegraphics{pic/p5/pu/1/img/testMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}
+			\includegraphics{pic/p5/sl/1/img/testMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}
+			\includegraphics{pic/p5/sa/1/img/testMap.eps}
+			\caption{}
+		\end{subfigure}
+		\caption{Validating set for (a) Pavia Center, (b) Pavia University, (c) Salinas Valley and (d) Salinas A}
+		\label{testMaps}
+	\end{figure}
 

### 2020-03-11 postProcess.py

@@ -111,6 +111,11 @@ class ProbMap:
 			# print(k,color)
 
 	def convertToColor(self,map):
+		unique = np.unique(map)
+		lut = np.zeros(np.max(unique) + 1, dtype=np.int)
+		for iter, i in enumerate(unique):
+			lut[i] = iter
+		map = lut[map]
 		a = np.zeros(shape=(np.shape(map)[0], np.shape(map)[1], 3), dtype=np.uint8)
 		for i in range(np.shape(map)[0]):
 			for j in range(np.shape(map)[1]):

### 2020-03-11 paper/paper.tex
fixed some bugs

@@
 	In this section, we showed and analyzed the training result.
-	We compared our model with six neural network based algorithms i.e., 1D CNN\cite{hu2015deep},
+	We compared our model with six neural network based algorithms i.e.,
+	1D CNN\cite{hu2015deep},
 	2D CNN\cite{sharma2016hyperspectral},
@@
 	In our experiment, we selected 4 real HSI dataset to train and test our DCCN model separately, that is, the
-	Pavia University dataset, the Pavia Center dataset, the Salinas Valley dataset and the Salinas A dataset, which is
-	a small subset of the Salinas Valley dataset.
+	Pavia University(PU) dataset, the Pavia Center(PC) dataset, the Salinas Valley(SV) dataset and the Salinas A(SA)
+	dataset, which is a small subset of the Salinas Valley dataset.
 	The first three of them are relatively large dataset and the last one is relatively small.
@@
 	\end{enumerate}
-	Usually, a HSI dataset has labeled and unlabeled pixels.
+
+	\subsection{Environment}\label{subsec:environment}
+	We trained and tested the model on a PC with 4 NVIDIA RTX 2080Ti(11GB) GPUs, dual Xeon 4210 Processor
+	and 128GB of memory.
+	The operating system is Ubuntu server 18.04 x64 LTS with CUDA 10.1 and CUDNN 7.6.5.
+	We implement the model with Tensorflow 1.14.0 and the model is trained and tested on GPU\@.
+
+	\subsection{Experiment Setup}Usually, a HSI dataset has labeled and unlabeled pixels.
 	In our experiment we discarded those unlabeled pixels, only using the labeled pixels for training and testing.
@@
 
-	\subsection{Environment}\label{subsec:environment}
-	We trained and tested the model on a PC with 4 NVIDIA RTX 2080Ti(11GB) GPUs, dual Xeon 4210 Processor
-	and 128GB of memory.
-	The operating system is Ubuntu server 18.04 x64 LTS\@.
-	We implement the model with Tensorflow 1.14.0 and the model is trained and tested on GPU\@.
+	\subsection{Result and Analysis}\label{subsec:result-and-analysis}
+	First of all, we listed the quantitative classification assessment using the PU, PC, SV and SA dataset considering
+	SVM,
+	1D CNN\cite{hu2015deep},
+	2D CNN\cite{sharma2016hyperspectral},
+	3D CNN\cite{hamida20183},
+	3D FCN\cite{lee2016contextual},
+	CNN-MRF\cite{cao2018hyperspectral},
+	CapsNet and DCCN together.
 
-	\subsection{Result and Analysis}\label{subsec:result-and-analysis}
+	\subsection{Convergence analysis}\label{subsec:convergence}
 
 	\section{DISCUSSION}\label{sec:discussion}
-
-	\subsection{Convergence analysis}\label{subsec:convergence}
 
@@
 \end{document}
+
+%Usually, a HSI dataset has labeled and unlabeled pixels.
+%	In our experiment we discarded those unlabeled pixels, only using the labeled pixels for training and testing.
+%	We divided the labeled pixels into 3 groups in our experiment: training data, testing data and validating data.
+%	We randomly selected 10\% of the total labeled pixels as training set, then we randomly selected 100 labeled pixels
+%	and the rest of the labeled pixels was used to validate the model.
+%	The training and validating dataset are shown in figure~\ref{trainMaps} and figure~\ref{testMaps}
+%
+%	\begin{figure}
+%		\begin{subfigure}
+%			\includegraphics{pic/p5/pc/1/img/trainMap.eps}
+%			\caption{}
+%		\end{subfigure}
+%		\begin{subfigure}
+%			\includegraphics{pic/p5/pu/1/img/trainMap.eps}
+%			\caption{}
+%		\end{subfigure}
+%		\begin{subfigure}
+%			\includegraphics{pic/p5/sl/1/img/trainMap.eps}
+%			\caption{}
+%		\end{subfigure}
+%		\begin{subfigure}
+%			\includegraphics{pic/p5/sa/1/img/trainMap.eps}
+%			\caption{}
+%		\end{subfigure}
+%		\caption{Training set for (a) Pavia Center, (b) Pavia University, (c) Salinas Valley and (d) Salinas A}
+%		\label{trainMaps}
+%	\end{figure}
+%
+%	\begin{figure}
+%		\begin{subfigure}
+%			\includegraphics{pic/p5/pc/1/img/testMap.eps}
+%			\caption{}
+%		\end{subfigure}
+%		\begin{subfigure}
+%			\includegraphics{pic/p5/pu/1/img/testMap.eps}
+%			\caption{}
+%		\end{subfigure}
+%		\begin{subfigure}
+%			\includegraphics{pic/p5/sl/1/img/testMap.eps}
+%			\caption{}
+%		\end{subfigure}
+%		\begin{subfigure}
+%			\includegraphics{pic/p5/sa/1/img/testMap.eps}
+%			\caption{}
+%		\end{subfigure}
+%		\caption{Validating set for (a) Pavia Center, (b) Pavia University, (c) Salinas Valley and (d) Salinas A}
+%		\label{testMaps}
+%	\end{figure}

### 2020-03-11 postProcess.py

@@ -112,7 +112,7 @@ class ProbMap:
 
 	def convertToColor(self,map):
 		unique = np.unique(map)
-		lut = np.zeros(np.max(unique) + 1, dtype=np.int)
+		lut = np.zeros((int)(np.max(unique) + 1), dtype=np.int)
 		for iter, i in enumerate(unique):
 			lut[i] = iter
 		map = lut[map]

### 2020-03-11 dataloader.py
fixed a big bug

@@ -89,6 +89,7 @@ class DataLoader:
 		for iter, i in enumerate(unique):
 			lut[i] = iter
 		self.label = lut[self.label]
+		# f=open("wtf3.txt","w+")
 		with tqdm(total=self.height * self.width, desc="slicing ", ncols=LENGTH, ascii=TQDM_ASCII) as pbar:
 			for i in range(self.height):
 				for j in range(self.width):
@@ -101,9 +102,10 @@ class DataLoader:
 					if tmpLabel != 0:
 						self.classPatches[tmpLabel - 1].append(tmpPatch)
 						self.classSpectrum[tmpLabel - 1].append(tmpSpectrum)
-						self.classIndex[tmpLabel - 1].append(i * self.height + j)
+						self.classIndex[tmpLabel - 1].append(i * self.width + j)
 					pbar.update(1)
 		# self.numEachClass.append(0)
+		# f.close()
 		for i in range(self.numClasses):
 			self.numEachClass.append(len(self.classIndex[i]))
 
@@ -249,7 +251,13 @@ class DataLoader:
 			patch.extend(self.classPatches[i][j] for j in range(self.numEachClass[i]))
 			spectrum.extend(self.classSpectrum[i][j] for j in range(self.numEachClass[i]))
 			index.extend(self.classIndex[i][j] for j in range(self.numEachClass[i]))
+			# print("hhh***", len(index), len(np.unique(index)),i)
 			label.extend(i for j in range(self.numEachClass[i]))
+		# with open("wtf4.txt","w+") as f:
+		# 	for i in self.classIndex:
+		# 		for j in i:
+		# 			print("%5d"%j,end=" ",file=f)
+		# 		print(file=f)
 		patch = np.array(patch)
 		spectrum = np.array(spectrum)
 		label = convertToOneHot(np.array(label))

### 2020-03-11 postProcess.py

@@ -111,10 +111,19 @@ class ProbMap:
 			# print(k,color)
 
 	def convertToColor(self,map):
+		# with open("seeData.txt","w+") as f:
+		# 	for i in map:
+		# 		for j in i :
+		# 			print("%3d"%j,end="",file=f)
+		# 		print(file=f)
+		map=np.array(map,dtype=int)
 		unique = np.unique(map)
 		lut = np.zeros((int)(np.max(unique) + 1), dtype=np.int)
-		for iter, i in enumerate(unique):
-			lut[i] = iter
+		for it, i in enumerate(unique):
+			# print(it,i)
+			lut[i] = it
+		# print(lut)
+		# print(unique)
 		map = lut[map]
 		a = np.zeros(shape=(np.shape(map)[0], np.shape(map)[1], 3), dtype=np.uint8)
 		for i in range(np.shape(map)[0]):
@@ -138,15 +147,23 @@ class ProbMap:
 		self.map = pickle.load(f)
 
 	def drawGt(self):
+		f=open("wtf.txt","w+")
 		plt.figure()
-		groundTruth = np.zeros(shape=(self.height, self.width))
+		groundTruth = np.zeros(shape=(self.height, self.width),dtype=int)
+		# print(self.height,self.width,"8888888888")
 		with tqdm(total=np.shape(self.groundTruth)[0], desc="processing gt", ascii=TQDM_ASCII) as pbar:
 			for i in range(np.shape(self.groundTruth)[0]):
 				index = self.index[i]
-				h = index // self.height
-				w = index % self.height
+				h = index // self.width
+				w = index % self.width
+				# print("%5d%5d%5d%5d"%(h,w,index,i),file=f)
+				# if groundTruth[h][w]!=0:
+				# 	print("*****",groundTruth[h][w],h,w,index,i,file=f)
 				groundTruth[h][w] += (self.groundTruth[i] + 1)
+				# print(groundTruth[h][w],file=f)
 				pbar.update()
+		# # print(np.unique(groundTruth),"*******")
+		# f.close()
 
 		groundTruth=self.convertToColor(groundTruth)
 		plt.imshow(groundTruth)
@@ -163,9 +180,9 @@ class ProbMap:
 		with tqdm(total=np.shape(self.groundTruth)[0], desc="processing gt", ascii=TQDM_ASCII) as pbar:
 			for i in range(np.shape(self.groundTruth)[0]):
 				index = self.index[i]
[…]

### 2020-03-11 train.py

@@ -217,7 +217,7 @@ with tf.Session() as sess:
 		trainProcess.drawLoss()
 		trainProcess.drawAcc()
 		probMap.drawProbMap()
-		probMap.drawGt()
 		probMap.drawPredictedMap()
 		probMap.drawTrainMap()
 		probMap.drawTestMap()
+		probMap.drawGt()

### 2020-03-11 paper/paper.tex
fixed a big bug

--- 2020-03-11 paper/paper.tex
@@
 \usepackage{xcolor}
+\usepackage{subfiles}
+\usepackage{subcaption}
 
@@
 	In our experiment, we selected 4 real HSI dataset to train and test our DCCN model separately, that is, the
-	Pavia University dataset, the Pavia Center dataset, the Salinas Valley dataset and the Salinas A dataset, which is
-	a small subset of the Salinas Valley dataset.
+	Pavia University(PU) dataset, the Pavia Center(PC) dataset, the Salinas Valley(SV) dataset and the Salinas A(SA)
+	dataset, which is a small subset of the Salinas Valley dataset.
 	The first three of them are relatively large dataset and the last one is relatively small.
 	We use these 4 dataset to test the robustness of out model when performing on different scale dataset.
-	Here follows the brief introduction of the four dataset.
+	Here follows the brief introduction of the four dataset(see table\ref{psgt}).
 	\begin{enumerate}[1)]
@@
 		The geometric resolution is 1.3 meters.
-		Both image has 9 different ground truth classes each(see table\ref{paviagt}).
+		Both image has 9 different ground truth classes each.
+		\item \textit{Salinas Scene} The Salinas scene was collected by the 224-band AVIRIS sensor over Salinas Valley,
+		California, and is characterized by high spatial resolution (3.7-meter pixels).
+		The Salinas Valley dataset is a 512*217 pixels image, and the Salinas A is a subset of the Salinas Valley
+		containing 86*83 pixels.
+		The Salinas scene dataset has been discarded 20 water absorption bands from the original image, so there's 204
+		bands left in both of the tow dataset.
+		The Salinas Valley dataset has 16 different classes but the Salinas A only has 6 different classes.
+	\end{enumerate}
 	\begin{table}[h]
 		\centering
-			\begin{tabular}{|c|c|}
+		\tiny
+		\resizebox{\textwidth}{!}{
+			\begin{tabular}{|c|c|c|c|}
+
 				\hline
-				\textbf{PAVIA CENTER}    & \textbf{PAVIA UNIVERSITY}\\
+				\textbf{PAVIA CENTER} & \textbf{PAVIA UNIVERSITY}&\textbf{SALINAS VALLEY}  & \textbf{SALINAS A}\\
 				\hline
 				\includegraphics[width=0.4\textwidth]{pic/pavia_gt.eps}&
-				\includegraphics[width=0.4\textwidth]{pic/paviaU_gt.eps}\\
+				\includegraphics[width=0.4\textwidth]{pic/paviaU_gt.eps}&
+				\includegraphics[width=0.4\textwidth]{pic/salinas_gt.eps}&
+				\includegraphics[width=0.4\textwidth]{pic/salinasA_gt.eps}\\
 				\hline
-				\begin{tabular}{ccc}
-					\footnotesize
+				\begin{tabular}[t]{ccc}
+
 					\textit{color}&\textit{land-cover type}&\textit{number}\\
@@
 				\end{tabular}&
-				\begin{tabular}{ccc}
-					\footnotesize
+				\begin{tabular}[t]{ccc}
+
 					\textit{color}&\textit{land-cover type}&\textit{number}\\
@@
 					\crule[paviaU9]{0.02\textwidth}{0.02\textwidth} &Shadows &947    \\
-				\end{tabular}\\
-				\hline
-			\end{tabular}
-			\caption{Number of samples in two Pavia scene dataset.}
-			\label{paviagt}
-		\end{table}
-		\item \textit{Salinas Scene} The Salinas scene was collected by the 224-band AVIRIS sensor over Salinas Valley,
-		California, and is characterized by high spatial resolution (3.7-meter pixels).
-		The Salinas Valley dataset is a 512*217 pixels image, and the Salinas A is a subset of the Salinas Valley
-		containing 86*83 pixels.
-		The Salinas scene dataset has been discarded 20 water absorption bands from the original image, so there's 204
-		bands left in both of the tow dataset.
-		The Salinas Valley dataset has 16 different classes but the Salinas A only has 6 different classes(see
-		table\ref{salinas_gt}).
-		\begin{table}[h]
-			\centering
-			\begin{tabular}{|c|c|}
-				\hline
-				\textbf{SALINAS VALLEY}  & \textbf{SALINAS A}\\
-				\hline
-				\includegraphics[width=0.4\textwidth]{pic/salinas_gt.eps}&
-				\includegraphics[width=0.4\textwidth]{pic/salinasA_gt.eps}\\
-				\hline
-				\begin{tabular}{ccc}
-					\footnotesize
+				\end{tabular}&
+				\begin{tabular}[t]{ccc}
+
 					\textit{color}&\textit{land-cover type}&\textit{number}\\
 					\hline
-					\crule[salinas_corrected1]{0.02\textwidth}{0.02\textwidth} &Brocoli green weeds-1 &2009  \\
-					\crule[salinas_corrected2]{0.02\textwidth}{0.02\textwidth} &Brocoli green weeds-2 &3726  \\
+					\crule[salinas_corrected1]{0.02\textwidth}{0.02\textwidth} &Brocoli green weeds 1 &2009  \\
+					\crule[salinas_corrected2]{0.02\textwidth}{0.02\textwidth} &Brocoli green weeds 2 &3726  \\
 					\crule[salinas_corrected3]{0.02\textwidth}{0.02\textwidth} &Fallow &1976  \\
@@
 					\crule[salinas_corrected10]{0.02\textwidth}{0.02\textwidth} &Corn senesced green weeds &3278  \\
-					\crule[salinas_corrected11]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-4wk &1068  \\
-					\crule[salinas_corrected12]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-5wk &1927  \\
-					\crule[salinas_corrected13]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-6wk &916  \\
-					\crule[salinas_corrected14]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-7wk &1070  \\
+					\crule[salinas_corrected11]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine 4wk &1068  \\
+					\crule[salinas_corrected12]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine 5wk &1927  \\
+					\crule[salinas_corrected13]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine 6wk &916  \\
+					\crule[salinas_corrected14]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine 7wk &1070  \\
 					\crule[salinas_corrected15]{0.02\textwidth}{0.02\textwidth} &Vinyard untrained &7268  \\
@@
 				\end{tabular}&
-				\begin{tabular}{ccc}
-					\footnotesize
+				\begin{tabular}[t]{ccc}
+
 					\textit{color}&\textit{land-cover type}&\textit{number}\\
 					\hline
-					\crule[salinasA_corrected1]{0.02\textwidth}{0.02\textwidth} &Brocoli green weeds-1 &391  \\
+					\crule[salinasA_corrected1]{0.02\textwidth}{0.02\textwidth} &Brocoli green weeds 1 &391  \\
 					\crule[salinasA_corrected2]{0.02\textwidth}{0.02\textwidth} &Corn senesced green weeds &1343  \\
-					\crule[salinasA_corrected3]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-4wk &616  \\
-					\crule[salinasA_corrected4]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-5wk &1525  \\
-					\crule[salinasA_corrected5]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-6wk &674  \\
-					\crule[salinasA_corrected6]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine-7wk &799  \\
-					\\
-					\\
-					\\
-					\\
-					\\
-					\\
-					\\
-					\\
-					\\
-					\\
+					\crule[salinasA_corrected3]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine 4wk &616  \\
+					\crule[salinasA_corrected4]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine 5wk &1525  \\
+					\crule[salinasA_corrected5]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine 6wk &674  \\
+					\crule[salinasA_corrected6]{0.02\textwidth}{0.02\textwidth} &Lettuce romaine 7wk &799  \\
 				\end{tabular}\\
 				\hline
-			\end{tabular}
-			\caption{Number of samples in the two Salinas scene dataset.}
-			\label{salinas_gt}
+
+			\end{tabular}}
+		\caption{Number of samples in two Pavia scene dataset.}
+		\label{psgt}
 	\end{table}
-	\end{enumerate}
 
@@
 	and 128GB of memory.
-	The operating system is Ubuntu server 18.04 x64 LTS\@.
+	The operating system is Ubuntu server 18.04 x64 LTS with CUDA 10.1 and CUDNN 7.6.5.
 	We implement the model with Tensorflow 1.14.0 and the model is trained and tested on GPU\@.
 
+	\subsection{Experiment Setup}Usually, a HSI dataset has labeled and unlabeled pixels.
+	In our experiment we discarded those unlabeled pixels, only using the labeled pixels for training and testing.
+	We divided the labeled pixels into 3 groups in our experiment: training data, testing data and validating data.
+	We randomly selected 10\% of the total labeled pixels as training set, then we randomly selected 100 labeled pixels
+	and the rest of the labeled pixels was used to validate the model.
+	The training and validating dataset are shown in figure~\ref{trainMaps} and figure~\ref{testMaps}
+
+	\begin{figure}[htbp]
+		\begin{subfigure}{0.24\textwidth}
+			\includegraphics[width=0.9\textwidth]{pic/p5/pc/1/img/trainMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.24\textwidth}
+			\includegraphics[width=0.9\textwidth]{pic/p5/pu/1/img/trainMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.24\textwidth}
+			\includegraphics[width=0.9\textwidth]{pic/p5/sl/1/img/trainMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.24\textwidth}
+			\includegraphics[width=0.9\textwidth]{pic/p5/sa/1/img/trainMap.eps}
+			\caption{}
+		\end{subfigure}
+		\caption{Training set for (a) Pavia Center, (b) Pavia University, (c) Salinas Valley and (d) Salinas A}
+		\label{trainMaps}
+	\end{figure}
+
+	\begin{figure}[htbp]
+		\begin{subfigure}{0.24\textwidth}
+			\includegraphics[width=0.9\textwidth]{pic/p5/pc/1/img/testMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.24\textwidth}
+			\includegraphics[width=0.9\textwidth]{pic/p5/pu/1/img/testMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.24\textwidth}
+			\includegraphics[width=0.9\textwidth]{pic/p5/sl/1/img/testMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.24\textwidth}
+			\includegraphics[width=0.9\textwidth]{pic/p5/sa/1/img/testMap.eps}
+			\caption{}
+		\end{subfigure}
+		\caption{Validating set for (a) Pavia Center, (b) Pavia University, (c) Salinas Valley and (d) Salinas A}
+		\label{testMaps}
+	\end{figure}
+
 	\subsection{Result and Analysis}\label{subsec:result-and-analysis}
+	First of all, we listed the quantitative classification assessment using the PU, PC, SV and SA dataset considering
+	SVM,
+	1D CNN\cite{hu2015deep},
+	2D CNN\cite{sharma2016hyperspectral},
+	3D CNN\cite{hamida20183},
+	3D FCN\cite{lee2016contextual},
+	CNN-MRF\cite{cao2018hyperspectral},
+	CapsNet and DCCN together in table~\ref{result}
+	\begin{table}[htb]
+		\tiny
+		\centering
+		\begin{tabular}{|c|c|c|c|c|}
+			\hline
+			 &\textbf{PAVIA CENTER} & \textbf{PAVIA UNIVERSITY}&\textbf{SALINAS VALLEY} & \textbf{SALINAS A}\\
+			\hline
+			\begin{tabular}{c}
+				\textbf{model}\\
+				\hline
+				{SVM}\\
+				{1D CNN\cite{hu2015deep}}\\
+				{2D CNN\cite{sharma2016hyperspectral}}\\
+				{3D CNN\cite{hamida20183}}\\
+				{3D FCN\cite{lee2016contextual}}\\
+				{CNN-MRF\cite{cao2018hyperspectral}}\\
+				{CapsNet}\\
+				{DCCN}\\
+			\end{tabular}&
+			\begin{tabular}{ccc}
+				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
+				\hline
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+			\end{tabular}&
+			\begin{tabular}{ccc}
+				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
+				\hline
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+			\end{tabular}&
+			\begin{tabular}{ccc}
+				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
+				\hline
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+			\end{tabular}&
+			\begin{tabular}{ccc}
+				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
+				\hline
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+				100\%&100\%&100\%\\
+			\end{tabular}\\
+			\hline
+		\end{tabular}
+		\caption{Final result of all adopted models.}
+	\end{table}\label{result}
+
+	\subsection{Convergence analysis}\label{subsec:convergence}
+	In this subsection, we evaluated the convergence of our proposed network.
+	Figure~\ref{accandloss}
+	\begin{figure}[htb]
+		\begin{subfigure}{0.24\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/lossAndAcc.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.24\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pu/1/img/lossAndAcc.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.24\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/sl/1/img/lossAndAcc.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.24\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/sa/1/img/lossAndAcc.eps}
+			\caption{}
+		\end{subfigure}
+		\caption{Accuracy and loss of the proposed DCCN model with increasing iterations during the training process.
+		The horizontal axis represents 100 training epochs.
+		The corresponding relationship between the plot and dataset are:(a) for Pavia Center, (b) for Pavia University,
+			(c) for Salinas Vallet and (d) for Salinas A}
+	\end{figure}\label{accandloss}
 
 	\section{DISCUSSION}\label{sec:discussion}
-
-	\subsection{Convergence analysis}\label{subsec:convergence}
 

### 2020-03-11 scripts/3090.sh

@@ -1,30 +1,30 @@
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p5/pu/1/ --model_path ./save/formal0311/model/DCCN/p5/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p5/pu/sum --draw
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p5/pu/2/ --model_path ./save/formal0311/model/DCCN/p5/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p5/pu/3/ --model_path ./save/formal0311/model/DCCN/p5/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p5/pu/4/ --model_path ./save/formal0311/model/DCCN/p5/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p5/pu/5/ --model_path ./save/formal0311/model/DCCN/p5/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p5/pu/sum --dont_save_data
[…]

### 2020-03-11 scripts/3091.sh

@@ -1,30 +1,30 @@
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p7/pu/1/ --model_path ./save/formal0311/model/DCCN/p7/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p7/pu/sum --draw
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p7/pu/2/ --model_path ./save/formal0311/model/DCCN/p7/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p7/pu/3/ --model_path ./save/formal0311/model/DCCN/p7/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p7/pu/4/ --model_path ./save/formal0311/model/DCCN/p7/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p7/pu/5/ --model_path ./save/formal0311/model/DCCN/p7/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p7/pu/sum --dont_save_data
[…]

### 2020-03-11 scripts/3092.sh

@@ -1,30 +1,30 @@
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p9/pu/1/ --model_path ./save/formal0311/model/DCCN/p9/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p9/pu/sum --draw
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p9/pu/2/ --model_path ./save/formal0311/model/DCCN/p9/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p9/pu/3/ --model_path ./save/formal0311/model/DCCN/p9/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p9/pu/4/ --model_path ./save/formal0311/model/DCCN/p9/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p9/pu/5/ --model_path ./save/formal0311/model/DCCN/p9/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p9/pu/sum --dont_save_data
[…]

### 2020-03-11 scripts/3093.sh

@@ -1,30 +1,30 @@
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p11/pu/1/ --model_path ./save/formal0311/model/DCCN/p11/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p11/pu/sum --draw
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p11/pu/2/ --model_path ./save/formal0311/model/DCCN/p11/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p11/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p11/pu/3/ --model_path ./save/formal0311/model/DCCN/p11/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p11/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p11/pu/4/ --model_path ./save/formal0311/model/DCCN/p11/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p11/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311/data/DCCN/p11/pu/5/ --model_path ./save/formal0311/model/DCCN/p11/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311/model/DCCN/p11/pu/sum --dont_save_data
[…]

### 2020-03-11 paper/paper.tex
write some paper

@@
 	CNN-MRF\cite{cao2018hyperspectral},
-	the CapsNet that is identical to our DCCN model except the spectral channel and the machine learning algorithm SVM\@.
-	The accuracy metrics we used includes overall accuracy(OA), average accuracy(AA) and Kappa Coefficient($\kappa$).
+	the CapsNet that is identical to our DCCN model except the spectral channel, and the machine learning algorithm
+	SVM\@.
+	The competing neural network based algorithms are trained using the best network structure and hyper-parameters
+	proposed by the authors in their papers, and the SVM algorithm was trained using 10\% of the total labeled pixels
+	as the DCCN model.
+	The accuracy metrics we used include overall accuracy(OA), average accuracy(AA) and Kappa Coefficient($\kappa$).
 
@@
 	We randomly selected 10\% of the total labeled pixels as training set, then we randomly selected 100 labeled pixels
-	and the rest of the labeled pixels was used to validate the model.
+	and all pixels except those chosen for training were used to validate the model.
 	The training and validating dataset are shown in figure~\ref{trainMaps} and figure~\ref{testMaps}
@@
 		\end{subfigure}
-		\caption{Validating set for (a) Pavia Center, (b) Pavia University, (c) Salinas Valley and (d) Salinas A}
+		\caption{Validating set for (a) Pavia Center, (b) Pavia University, (c) Salinas Valley and (d) Salinas A.}
 		\label{testMaps}
@@
 	CNN-MRF\cite{cao2018hyperspectral},
-	CapsNet and DCCN together in table~\ref{result}
+	CapsNet and DCCN together in table~\ref{result}.
+	From the results reported in table~\ref{result}, we can observe that our proposed DCCN model outperforms all the
+	other seven state-of-art models on all 4 dataset.
+	Among all competitors in this experiment, 3D CNN\cite{hamida20183} and the CapsNet model performed relatively second
+	best, since both of the two model achieved second high accuracy on different dataset.
+	This is expected because both of the two algorithm are spectral-spatial based so they can utilize more information,
+	compared to the 2D CNN, FCN, SVM and CNN-MRF classifiers, to classify the HSI pixels.
+	Nevertheless, our DCCN model can consistently outperform the second-best algorithm with an average \textbf{fill data
+	here} for AA, OA, $\kappa$.
+
 	\begin{table}[htb]
@@
 		\caption{Final result of all adopted models.}
-	\end{table}\label{result}
+		\label{result}
+	\end{table}
+
+	In figure~\ref{pupm,pcpm,svpm,sapm} we presented the classification maps outputted by our DCCN and seven competitor
+	model after the training process.
+	\begin{figure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\label{pcpm}
+	\end{figure}
+	\begin{figure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\label{pupm}
+	\end{figure}
+	\begin{figure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\label{svpm}
+	\end{figure}
+	\begin{figure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+			\caption{}
+		\end{subfigure}
+		\label{sapm}
+	\end{figure}
+
+	Finally, we presented the probability maps the eight algorithms produced of the four HSI dataset in
+	figure~\ref{pcpd ,pupd,svpd,sapd}.
+	\begin{figure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\label{pcpd}
+	\end{figure}
+	\begin{figure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\label{pupd}
+	\end{figure}
+	\begin{figure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\label{svpd}
+	\end{figure}
+	\begin{figure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\begin{subfigure}{0.125\textwidth}
+			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+			\caption{}
+		\end{subfigure}
+		\label{sapd}
+	\end{figure}
 
@@
 	In this subsection, we evaluated the convergence of our proposed network.
-	Figure~\ref{accandloss}
+	Figure~\ref{accandloss} showed the training process of our DCCN model for 4 dataset separately.
 	\begin{figure}[htb]
@@
 		The corresponding relationship between the plot and dataset are:(a) for Pavia Center, (b) for Pavia University,
-			(c) for Salinas Vallet and (d) for Salinas A}
-	\end{figure}\label{accandloss}
+			(c) for Salinas Vallet and (d) for Salinas A.}
+		\label{accandloss}
+	\end{figure}
 
 	\section{DISCUSSION}\label{sec:discussion}
+	In this sector, we further explored the effect of different hyper-parameters to the DCCN\@.
+	We used the Pavia University and Salinas A dataset to train and test our model, so that we can observe the model's
+	performance on both large and small dataset.
+	We first tested the effect of different size of training set with a fixed patch size of 7*7, and then tested the
+	effect of
 

### 2020-03-11 scripts/3090.sh
fixed some bugs

@@ -1,30 +1,20 @@
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p5/pu/1/ --model_path ./save/formal0311-1/model/DCCN/p5/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p5/pu/sum --draw
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p5/pu/2/ --model_path ./save/formal0311-1/model/DCCN/p5/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p5/pu/3/ --model_path ./save/formal0311-1/model/DCCN/p5/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p5/pu/4/ --model_path ./save/formal0311-1/model/DCCN/p5/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p5/pu/5/ --model_path ./save/formal0311-1/model/DCCN/p5/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p5/pu/sum --dont_save_data
-
[…]

### 2020-03-11 scripts/3091.sh

@@ -1,30 +1,20 @@
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p7/pu/1/ --model_path ./save/formal0311-1/model/DCCN/p7/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p7/pu/sum --draw
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p7/pu/2/ --model_path ./save/formal0311-1/model/DCCN/p7/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p7/pu/3/ --model_path ./save/formal0311-1/model/DCCN/p7/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p7/pu/4/ --model_path ./save/formal0311-1/model/DCCN/p7/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p7/pu/5/ --model_path ./save/formal0311-1/model/DCCN/p7/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p7/pu/sum --dont_save_data
-
[…]

### 2020-03-11 scripts/3092.sh

@@ -1,30 +1,20 @@
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p9/pu/1/ --model_path ./save/formal0311-1/model/DCCN/p9/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p9/pu/sum --draw
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p9/pu/2/ --model_path ./save/formal0311-1/model/DCCN/p9/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p9/pu/3/ --model_path ./save/formal0311-1/model/DCCN/p9/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p9/pu/4/ --model_path ./save/formal0311-1/model/DCCN/p9/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p9/pu/5/ --model_path ./save/formal0311-1/model/DCCN/p9/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p9/pu/sum --dont_save_data
-
[…]

### 2020-03-11 scripts/3093.sh

@@ -1,30 +1,20 @@
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p11/pu/1/ --model_path ./save/formal0311-1/model/DCCN/p11/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p11/pu/sum --draw
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p11/pu/2/ --model_path ./save/formal0311-1/model/DCCN/p11/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p11/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p11/pu/3/ --model_path ./save/formal0311-1/model/DCCN/p11/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p11/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p11/pu/4/ --model_path ./save/formal0311-1/model/DCCN/p11/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p11/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p11/pu/5/ --model_path ./save/formal0311-1/model/DCCN/p11/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/model/DCCN/p11/pu/sum --dont_save_data
-
[…]

### 2020-03-12 postProcess.py
fixed some bugs

@@ -120,10 +120,7 @@ class ProbMap:
 		unique = np.unique(map)
 		lut = np.zeros((int)(np.max(unique) + 1), dtype=np.int)
 		for it, i in enumerate(unique):
-			# print(it,i)
 			lut[i] = it
-		# print(lut)
-		# print(unique)
 		map = lut[map]
 		a = np.zeros(shape=(np.shape(map)[0], np.shape(map)[1], 3), dtype=np.uint8)
 		for i in range(np.shape(map)[0]):

### 2020-03-12 scripts/3090.sh

@@ -1,20 +1,20 @@
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p5/pu/1/ --model_path ./save/formal0311-1/model/DCCN/p5/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p5/pu/sum --draw
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p5/pu/2/ --model_path ./save/formal0311-1/model/DCCN/p5/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p5/pu/3/ --model_path ./save/formal0311-1/model/DCCN/p5/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p5/pu/4/ --model_path ./save/formal0311-1/model/DCCN/p5/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p5/pu/5/ --model_path ./save/formal0311-1/model/DCCN/p5/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p5/pu/sum --dont_save_data
[…]

### 2020-03-12 scripts/3091.sh

@@ -1,20 +1,20 @@
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p7/pu/1/ --model_path ./save/formal0311-1/model/DCCN/p7/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p7/pu/sum --draw
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p7/pu/2/ --model_path ./save/formal0311-1/model/DCCN/p7/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p7/pu/3/ --model_path ./save/formal0311-1/model/DCCN/p7/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p7/pu/4/ --model_path ./save/formal0311-1/model/DCCN/p7/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p7/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p7/pu/5/ --model_path ./save/formal0311-1/model/DCCN/p7/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p7/pu/sum --dont_save_data
[…]

### 2020-03-12 scripts/3092.sh

@@ -1,20 +1,20 @@
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p9/pu/1/ --model_path ./save/formal0311-1/model/DCCN/p9/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p9/pu/sum --draw
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p9/pu/2/ --model_path ./save/formal0311-1/model/DCCN/p9/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p9/pu/3/ --model_path ./save/formal0311-1/model/DCCN/p9/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p9/pu/4/ --model_path ./save/formal0311-1/model/DCCN/p9/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p9/pu/sum --dont_save_data
-python ./train.py -g 2 -e 100 --data 2 -l 0.0001 -p 9 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p9/pu/5/ --model_path ./save/formal0311-1/model/DCCN/p9/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p9/pu/sum --dont_save_data
[…]

### 2020-03-12 scripts/3093.sh

@@ -1,20 +1,20 @@
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p11/pu/1/ --model_path ./save/formal0311-1/model/DCCN/p11/pu/1/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p11/pu/sum --draw
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p11/pu/2/ --model_path ./save/formal0311-1/model/DCCN/p11/pu/2/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p11/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p11/pu/3/ --model_path ./save/formal0311-1/model/DCCN/p11/pu/3/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p11/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p11/pu/4/ --model_path ./save/formal0311-1/model/DCCN/p11/pu/4/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p11/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 11 -r 0.1 -m 1 -d ./save/formal0311-1/data/DCCN/p11/pu/5/ --model_path ./save/formal0311-1/model/DCCN/p11/pu/5/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/formal0311-1/data/DCCN/p11/pu/sum --dont_save_data
[…]

### 2020-03-12 paper/paper.tex
fixed some bugs

@@
 	We compared our model with six neural network based algorithms i.e.,
-	1D CNN\cite{hu2015deep},
-	2D CNN\cite{sharma2016hyperspectral},
+	semi-supervised 2D CNN\cite{liu2017semi},
 	3D CNN\cite{hamida20183},
+	multi-scale 3D CNN(3D CNN-MS)\cite{he2017multi},
 	3D FCN\cite{lee2016contextual},
@@
 	as the DCCN model.
+	In order to reduce the effect of accidental errors, we did the same experiment with identical parameters five times
+	on each model.
 	The accuracy metrics we used include overall accuracy(OA), average accuracy(AA) and Kappa Coefficient($\kappa$).
@@
 		The number of spectral bands is 102 for Pavia Centre and 103 for Pavia University.
-		Pavia Centre is a 1096*1096 pixels image, and Pavia University is 610*610 pixels, but some of the samples in
+		Pavia Centre is a 1096×1096 pixels image, and Pavia University is 610×610 pixels, but some of the samples in
 		both images contain no information and have to be discarded before the analysis, so the final picture size is
-		1096*715 and 610*340.
+		1096×715 and 610×340.
 		The geometric resolution is 1.3 meters.
@@
 		California, and is characterized by high spatial resolution (3.7-meter pixels).
-		The Salinas Valley dataset is a 512*217 pixels image, and the Salinas A is a subset of the Salinas Valley
-		containing 86*83 pixels.
+		The Salinas Valley dataset is a 512×217 pixels image, and the Salinas A is a subset of the Salinas Valley
+		containing 86×83 pixels.
 		The Salinas scene dataset has been discarded 20 water absorption bands from the original image, so there's 204
@@
 	1D CNN\cite{hu2015deep},
-	2D CNN\cite{sharma2016hyperspectral},
+	2D CNN\cite{liu2017semi},
 	3D CNN\cite{hamida20183},
@@
 				{1D CNN\cite{hu2015deep}}\\
-				{2D CNN\cite{sharma2016hyperspectral}}\\
+				{2D CNN\cite{liu2017semi}}\\
 				{3D CNN\cite{hamida20183}}\\
@@
 	\begin{figure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/predictMap.eps}
 			\caption{}
 		\end{subfigure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/predictMap.eps}
 			\caption{}
 		\end{subfigure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/predictMap.eps}
 			\caption{}
 		\end{subfigure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/predictMap.eps}
 			\caption{}
 		\end{subfigure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/predictMap.eps}
 			\caption{}
 		\end{subfigure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/predictMap.eps}
 			\caption{}
 		\end{subfigure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/predictMap.eps}
 			\caption{}
 		\end{subfigure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/predictMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/predictMap.eps}
 			\caption{}
@@
 	\begin{figure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/probMap.eps}
 			\caption{}
 		\end{subfigure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/probMap.eps}
 			\caption{}
 		\end{subfigure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/probMap.eps}
 			\caption{}
 		\end{subfigure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/probMap.eps}
 			\caption{}
 		\end{subfigure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/probMap.eps}
 			\caption{}
 		\end{subfigure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/probMap.eps}
 			\caption{}
 		\end{subfigure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/probMap.eps}
 			\caption{}
 		\end{subfigure}
-		\begin{subfigure}{0.125\textwidth}
-			\includegraphics[width=0.95\textwidth]{pic/p5/pc/1/img/probMap.eps}
+		\begin{subfigure}{0.12\textwidth}
+			\includegraphics[width=\textwidth]{pic/p5/pc/1/img/probMap.eps}
 			\caption{}
@@
 	performance on both large and small dataset.
-	We first tested the effect of different size of training set with a fixed patch size of 7*7, and then tested the
-	effect of
+	We first tested the effect of different size of training set with a fixed patch size of 7×7, and then tested the
+	effect of different patch sizes.
 

### 2020-03-12 calmetric.py

@@ -1,0 +1,37 @@
+import argparse
+import numpy as np
+import re
+
+if __name__ == "__main__":
+	parser = argparse.ArgumentParser()
+	parser.add_argument("-d", "--directory")
+	args = parser.parse_args()
+	"./save/0312309/dccn/p7/pc/sum/sum.txt"
+	with open("./save/0312/he/sa/data/sum.txt", "r") as f:
+		aa = []
+		oa = []
+		kappa = []
+		for line in f.readlines():
+			wordlist = re.split(", |:| ",line.strip())
+			# print(wordlist)
+			oa.append((float)(wordlist[0]))
+			aa.append((float)(wordlist[1]))
+			kappa.append((float)(wordlist[2]))
+		# print(aa)
+		# print(oa)
+		# print(kappa)
+		# exit()
+		oamid = (np.max(oa) + np.min(oa)) / 2
+		oadiff = oamid - np.min(oa)
+		aamid = (np.max(aa) + np.min(aa)) / 2
+		aadiff = aamid - np.min(aa)
+		kpmid = (np.max(kappa) + np.min(kappa)) / 2
+		kpdiff = kpmid - np.min(kappa)
+		# oamid *=100
+		# oadiff *=100
+		aamid *=100
+		aadiff *=100
+		kpmid *=100
+		kpdiff *=100
+
+		print("%.2f±%.2f & %.2f±%.2f & %.2f±%.2f\\\\" % (oamid, oadiff, aamid, aadiff, kpmid, kpdiff))

### 2020-03-12 dataloader.py

@@ -46,7 +46,7 @@ class DataLoader:
 		# print(self.height,self.width,self.bands)
 
 		self.__slice()
-		with open("seeData.txt", "w+") as f:
+		with open("txt/seeData.txt", "w+") as f:
 			last = np.shape(self.allPatch[0])
 			for a, i in enumerate(self.allPatch):
 				if last != np.shape(i):

### 2020-03-12 postProcess.py

@@ -144,7 +144,7 @@ class ProbMap:
 		self.map = pickle.load(f)
 
 	def drawGt(self):
-		f=open("wtf.txt","w+")
+		f=open("txt/wtf.txt", "w+")
 		plt.figure()
 		groundTruth = np.zeros(shape=(self.height, self.width),dtype=int)
 		# print(self.height,self.width,"8888888888")
@@ -301,7 +301,7 @@ if __name__ == "__main__":
 	probMap = ProbMap(dataloader.numClasses, ".\\save\\formal0311\\data\\DCCN\\p5\\sa\\1",
 	                  allLabeledLabel, allLabeledIndex, dataloader.height, dataloader.width, dataloader.trainIndex)
 	probMap.restore()
-	with open("seeData.txt","w+") as f:
+	with open("txt/seeData.txt", "w+") as f:
 		for i in dataloader.label:
 			for j in i :
 				print("%3d"%j,end="",file=f)

### 2020-03-12 paper/paper.tex
fixed some bugs

@@
 		\centering
-		\begin{tabular}{|c|c|c|c|c|}
+		\resizebox{\textwidth}{!}{
+			\begin{tabular}{c|c|c|c|c}
 				\hline
-			 &\textbf{PAVIA CENTER} & \textbf{PAVIA UNIVERSITY}&\textbf{SALINAS VALLEY} & \textbf{SALINAS A}\\
+				no item&\textbf{PAVIA CENTER} & \textbf{PAVIA UNIVERSITY}&\textbf{SALINAS VALLEY} & \textbf{SALINAS A}\\
 				\hline
 				\begin{tabular}{c}
-				\textbf{model}\\
+					\textbf{metrics}\\
 					\hline
 					{SVM}\\
-				{1D CNN\cite{hu2015deep}}\\
 					{2D CNN\cite{liu2017semi}}\\
 					{3D CNN\cite{hamida20183}}\\
+					{3D CNN-MS\cite{he2017multi}}\\
 					{3D FCN\cite{lee2016contextual}}\\
@@
 				\begin{tabular}{ccc}
-				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
+					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
 					\hline
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
+					97.52±0.07 & 91.74±0.33 & 96.49±0.10\\%{SVM}\\
+					98.27±0.14 & 97.24±0.54 & 97.56±0.19\\%{2D CNN\cite{liu2017semi}}\\
+					95.25±2.99 & 89.74±7.37 & 93.32±4.21\\%{3D CNN\cite{hamida20183}}\\
+					98.03±0.40 & 96.31±1.42 & 97.22±0.56\\%{3D CNN\cite{he2017multi}}\\
+					98.33±0.59 & 94.65±2.09 & 97.64±0.83\\%{3D FCN\cite{lee2016contextual}}\\
+					99.24±0.23 & 97.54±1.04 & 98.92±0.33\\%{CNN-MRF\cite{cao2018hyperspectral}}\\
+					99.48±0.09 & 98.50±0.21 & 99.27±0.12\\%{CapsNet}\\
+					\textbf{99.53±0.02} & \textbf{98.59±0.20} & \textbf{99.34±0.03}\\%{DCCN}\\
 				\end{tabular}&
 				\begin{tabular}{ccc}
-				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
+					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
 					\hline
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
+					79.86±0.26 & 64.26±0.45 & 71.86±0.39\\%{SVM}\\
+					93.74±0.42 & 95.61±0.79 & 91.85±0.54\\%{2D CNN\cite{liu2017semi}}\\
+					77.92±12.22 & 85.34±7.42 & 73.42±13.63\\%{3D CNN\cite{hamida20183}}\\
+					93.39±1.34 & 95.97±1.39 & 91.42±1.72\\%{3D CNN\cite{he2017multi}}\\
+					88.45±1.66 & 85.58±3.22 & 84.49±2.22\\%{3D FCN\cite{lee2016contextual}}\\
+					98.07±0.62 & 96.80±1.06 & 97.44±0.82\\%{CNN-MRF\cite{cao2018hyperspectral}}\\
+					97.69±0.60 & 96.82±0.83 & 96.94±0.80\\%{DCCN}\\
+					\textbf{98.40±0.19} & \textbf{97.77±0.33} & \textbf{97.89±0.25}\\%{CapsNet}\\
 				\end{tabular}&
 				\begin{tabular}{ccc}
-				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
+					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
 					\hline
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
+					82.45±0.75 & 86.16±0.93 & 80.24±0.87\\%{SVM}\\
+					92.24±1.19 & 95.82±0.61 & 91.36±1.34\\%{2D CNN\cite{liu2017semi}}\\
+					88.27±4.18 & 92.76±2.96 & 86.87±4.74\\%{3D CNN\cite{hamida20183}}\\
+					91.29±2.91 & 95.08±1.68 & 90.28±3.27\\%{3D CNN\cite{he2017multi}}\\
+					87.11±3.77 & 90.10±3.66 & 85.57±4.28\\%{3D FCN\cite{lee2016contextual}}\\
+					94.69±1.48 & 97.39±0.80 & 94.07±1.66\\%{CNN-MRF\cite{cao2018hyperspectral}}\\
+					94.48±0.59 & 96.84±0.58 & 93.83±0.66\\%{DCCN}\\
+					\textbf{95.00±0.59} & \textbf{97.30±0.50} & \textbf{94.42±0.66}\\%{CapsNet}\\
 				\end{tabular}&
 				\begin{tabular}{ccc}
-				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
+					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
 					\hline
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
+					97.44±0.19 & 97.42±0.22 & 96.80±0.23\\%{SVM}\\
+					84.47±0.51 & 89.86±0.69 & 81.22±0.62\\%{2D CNN\cite{liu2017semi}}\\
+					79.27±4.74 & 80.81±8.80 & 74.70±5.96\\%{3D CNN\cite{hamida20183}}\\
+					79.92±4.91 & 85.46±5.01 & 75.99±5.69\\%{3D CNN\cite{he2017multi}}\\
+					86.54±3.72 & 85.55±4.30 & 83.09±4.65\\%{3D FCN\cite{lee2016contextual}}\\
+					98.00±1.61 & 97.10±2.33 & 97.48±2.03\\%{CNN-MRF\cite{cao2018hyperspectral}}\\
+					99.52±0.10 & 99.31±0.15 & 99.40±0.13\\%{CapsNet}\\
+					\textbf{99.56±0.05} & \textbf{99.36±0.07} & \textbf{99.45±0.06}\\%{DCCN}\\
 				\end{tabular}\\
-			\hline
 			\end{tabular}
-		\caption{Final result of all adopted models.}
-		\label{result}
+		}
 	\end{table}

### 2020-03-12 calmetric.py

@@ -7,7 +7,7 @@ if __name__ == "__main__":
 	parser.add_argument("-d", "--directory")
 	args = parser.parse_args()
 	"./save/0312309/dccn/p7/pc/sum/sum.txt"
-	with open("./save/0312/he/sa/data/sum.txt", "r") as f:
+	with open("./save/0312/liu/pc/data/sum.txt", "r") as f:
 		aa = []
 		oa = []
 		kappa = []

### 2020-03-12 model.py

@@ -1,6 +1,7 @@
 import tensorflow as tf
 import capslayer as cl
 import numpy as np
+from tensorflow.contrib import slim
 
 
 def DCCapsNet(patch, spectrum, k, output, firstDimension=6,secondDimension=8):
@@ -98,3 +99,18 @@ def CapsNet(net, output):
 		routing_method="DynamicRouting"
 	)
 	return rt_probs
+
+def conv_net(net,num_classes):
+	with slim.arg_scope([slim.conv2d, slim.fully_connected],
+	                    activation_fn=tf.nn.relu):
+		net = slim.conv2d(net, 300, 3, padding='VALID',
+		                  weights_initializer=tf.contrib.layers.xavier_initializer())
+		net = slim.max_pool2d(net,2,padding='SAME')
+		net = slim.conv2d(net, 200, 3, padding='VALID',
+		                  weights_initializer=tf.contrib.layers.xavier_initializer())
+		net = slim.max_pool2d(net,2,padding='SAME')
+		net = slim.flatten(net)
+		net = slim.fully_connected(net,200)
+		net = slim.fully_connected(net,100)
+		logits = slim.fully_connected(net, num_classes, activation_fn=None)
+	return logits

### 2020-03-12 run.sh

@@ -1,13 +1,20 @@
-python ./train.py --data 1 -e 50 -r 0.1 -a 2 -l 0.0001 -m 1 --draw -d ./save/data/mar2/DCCN/id --model_path ./save/model/mar2/DCCN/id -g 1
-python ./train.py --data 2 -e 50 -r 0.1 -a 2 -l 0.0001 -m 1 --draw -d ./save/data/mar2/DCCN/pu --model_path ./save/model/mar2/DCCN/pu -g 1
-python ./train.py --data 3 -e 50 -r 0.1 -a 2 -l 0.0001 -m 1 --draw -d ./save/data/mar2/DCCN/pc --model_path ./save/model/mar2/DCCN/pc -g 1
-python ./train.py --data 4 -e 50 -r 0.1 -a 2 -l 0.0001 -m 1 --draw -d ./save/data/mar2/DCCN/sl --model_path ./save/model/mar2/DCCN/sl -g 1
-python ./train.py --data 5 -e 50 -r 0.1 -a 2 -l 0.0001 -m 1 --draw -d ./save/data/mar2/DCCN/SA --model_path ./save/model/mar2/DCCN/SA -g 1
-python ./train.py --data 6 -e 50 -r 0.1 -a 2 -l 0.0001 -m 1 --draw -d ./save/data/mar2/DCCN/KS --model_path ./save/model/mar2/DCCN/KS -g 1
-
-python ./train.py --data 1 -e 50 -r 0.1 -a 2 -l 0.0001 -m 2 --draw -d ./save/data/mar2/Caps/id --model_path ./save/model/mar2/Caps/id -g 1
-python ./train.py --data 2 -e 50 -r 0.1 -a 2 -l 0.0001 -m 2 --draw -d ./save/data/mar2/Caps/pu --model_path ./save/model/mar2/Caps/pu -g 1
-python ./train.py --data 3 -e 50 -r 0.1 -a 2 -l 0.0001 -m 2 --draw -d ./save/data/mar2/Caps/pc --model_path ./save/model/mar2/Caps/pc -g 1
-python ./train.py --data 4 -e 50 -r 0.1 -a 2 -l 0.0001 -m 2 --draw -d ./save/data/mar2/Caps/sl --model_path ./save/model/mar2/Caps/sl -g 1
-python ./train.py --data 5 -e 50 -r 0.1 -a 2 -l 0.0001 -m 2 --draw -d ./save/data/mar2/Caps/SA --model_path ./save/model/mar2/Caps/SA -g 1
[…]

### 2020-03-12 scripts/2020.sh

@@ -1,38 +1,52 @@
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2020/ --model_path ./save/mar4-2020/ --data 2 --first_layer 6 --second_layer 6 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2020/ --model_path ./save/mar4-2020/ --data 2 --first_layer 6 --second_layer 8 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2020/ --model_path ./save/mar4-2020/ --data 2 --first_layer 6 --second_layer 10 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2020/ --model_path ./save/mar4-2020/ --data 2 --first_layer 6 --second_layer 12 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2020/ --model_path ./save/mar4-2020/ --data 2 --first_layer 6 --second_layer 14 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2020/ --model_path ./save/mar4-2020/ --data 2 --first_layer 6 --second_layer 16 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2020/ --model_path ./save/mar4-2020/ --data 2 --first_layer 8 --second_layer 6 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 0 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2020/ --model_path ./save/mar4-2020/ --data 2 --first_layer 8 --second_layer 8 --dont_save_data --no_detailed_summary
[…]

### 2020-03-12 scripts/2021.sh

@@ -1,38 +1,51 @@
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2021/ --model_path ./save/mar4-2021/ --data 4 --first_layer 10 --second_layer 10 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2021/ --model_path ./save/mar4-2021/ --data 4 --first_layer 10 --second_layer 12 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2021/ --model_path ./save/mar4-2021/ --data 4 --first_layer 10 --second_layer 14 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2021/ --model_path ./save/mar4-2021/ --data 4 --first_layer 10 --second_layer 16 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2021/ --model_path ./save/mar4-2021/ --data 4 --first_layer 12 --second_layer 6 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2021/ --model_path ./save/mar4-2021/ --data 4 --first_layer 12 --second_layer 8 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2021/ --model_path ./save/mar4-2021/ --data 4 --first_layer 12 --second_layer 10 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0001 -g 1 -r 0.1 -a 1 -p 7 -m 1 -d ./save/mar4-2021/ --model_path ./save/mar4-2021/ --data 4 --first_layer 12 --second_layer 12 --dont_save_data --no_detailed_summary
[…]

### 2020-03-12 scripts/2022.sh

@@ -1,42 +1,30 @@
-python ./train.py -e 50 -b 50 -l 0.0005 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2022/ --model_path ./save/mar4-2022/ --data 5 --first_layer 8 --second_layer 6 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2022/ --model_path ./save/mar4-2022/ --data 5 --first_layer 8 --second_layer 8 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2022/ --model_path ./save/mar4-2022/ --data 5 --first_layer 8 --second_layer 10 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2022/ --model_path ./save/mar4-2022/ --data 5 --first_layer 8 --second_layer 12 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2022/ --model_path ./save/mar4-2022/ --data 5 --first_layer 8 --second_layer 14 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2022/ --model_path ./save/mar4-2022/ --data 5 --first_layer 8 --second_layer 16 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2022/ --model_path ./save/mar4-2022/ --data 5 --first_layer 10 --second_layer 6 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 2 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2022/ --model_path ./save/mar4-2022/ --data 5 --first_layer 10 --second_layer 8 --dont_save_data --no_detailed_summary
[…]

### 2020-03-12 scripts/2023.sh

@@ -1,38 +1,31 @@
-python ./train.py -e 50 -b 50 -l 0.0005 -g 3 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2023/ --model_path ./save/mar4-2023/ --data 2 --first_layer 10 --second_layer 14 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 3 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2023/ --model_path ./save/mar4-2023/ --data 2 --first_layer 10 --second_layer 16 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 3 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2023/ --model_path ./save/mar4-2023/ --data 2 --first_layer 12 --second_layer 6 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 3 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2023/ --model_path ./save/mar4-2023/ --data 2 --first_layer 12 --second_layer 8 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 3 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2023/ --model_path ./save/mar4-2023/ --data 2 --first_layer 12 --second_layer 10 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 3 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2023/ --model_path ./save/mar4-2023/ --data 2 --first_layer 12 --second_layer 12 --dont_save_data --no_detailed_summary
-python ./train.py -e 50 -b 50 -l 0.0005 -g 3 -r 0.1 -a 1 -p 9 -m 1 -d ./save/mar4-2023/ --model_path ./save/mar4-2023/ --data 2 --first_layer 12 --second_layer 14 --dont_save_data --no_detailed_summary
[…]

### 2020-03-12 train.py

@@ -5,7 +5,7 @@ import capslayer as cl
 import os
 import argparse
 from dataloader import DataLoader
-from model import DCCapsNet, CapsNet
+from model import DCCapsNet, CapsNet, conv_net
 from utils import LENGTH, calOA, selectData, calMixMatrix, calAA, calKappa, TQDM_ASCII
 from postProcess import TrainProcess, ProbMap
 
@@ -82,9 +82,12 @@ k = tf.placeholder(dtype=tf.float32)
 if args.model == 1:
 	pred = DCCapsNet(x, w, k, dataloader.numClasses, FIRST_LAYER, SECOND_LAYER)
 	print("USING DCCAPS***************************************")
-else:
+elif args.model==2:
 	pred = CapsNet(x, dataloader.numClasses)
 	print("USING CAPS*****************************************")
+else:
+	pred=conv_net(x,dataloader.numClasses)
+	print("USING CONV*****************************************")
 pred = tf.divide(pred, tf.reduce_sum(pred, 1, keep_dims=True))
 
 loss = tf.reduce_mean(cl.losses.margin_loss(y, pred))

### 2020-03-13 paper/paper.tex
draw dome

--- 2020-03-12 paper/paper.tex
@@
 	channels and then concatenates and feds the features into the capsule layer to classify each of the HSI pixels.
-	The model is trained and tested on \textbf{(2/3/4/5?)} real HSI dataset \textbf{(Pavia University, Pavia City,
-	Salinas Valley, Salinas A and KSC)} and achieved high accuracy.
-	We also compared our network with some of the state-of-art models and found our model outperformed these models.
-	Among these state-of-art models we also implemented the Capsule Network that has the same architecture as our
+	The model is trained and tested on four real HSI dataset, i.e., Pavia University, Pavia City,
+	Salinas Valley and Salinas A, and achieved high accuracy.
+	Moreover, our DCCN model has much higher confident for the predicted accuracy compared to the competitor algorithms.
+	We also compared our network with some of the state-of-the-art models and found our model outperformed these models.
+	Among these state-of-the-art models we also implemented the Capsule Network that has the same architecture as our
 	network except the spectral convolution channel, and we found the DCCN model was superior to it as well.
@@
 	\subsection{Dataset Introduction}\label{subsec:dataset-introduction}
-	In our experiment, we selected 4 real HSI dataset to train and test our DCCN model separately, that is, the
-	Pavia University(PU) dataset, the Pavia Center(PC) dataset, the Salinas Valley(SV) dataset and the Salinas A(SA)
-	dataset, which is a small subset of the Salinas Valley dataset.
-	The first three of them are relatively large dataset and the last one is relatively small.
-	We use these 4 dataset to test the robustness of out model when performing on different scale dataset.
-	Here follows the brief introduction of the four dataset(see table\ref{psgt}).
-	\begin{enumerate}[1)]
-		\item \textit{Pavia Center and University} These are two scenes acquired by the ROSIS sensor during a flight
-		campaign over Pavia, northern Italy.
-		The number of spectral bands is 102 for Pavia Centre and 103 for Pavia University.
-		Pavia Centre is a 1096×1096 pixels image, and Pavia University is 610×610 pixels, but some of the samples in
-		both images contain no information and have to be discarded before the analysis, so the final picture size is
-		1096×715 and 610×340.
-		The geometric resolution is 1.3 meters.
-		Both image has 9 different ground truth classes each.
-		\item \textit{Salinas Scene} The Salinas scene was collected by the 224-band AVIRIS sensor over Salinas Valley,
-		California, and is characterized by high spatial resolution (3.7-meter pixels).
-		The Salinas Valley dataset is a 512×217 pixels image, and the Salinas A is a subset of the Salinas Valley
-		containing 86×83 pixels.
-		The Salinas scene dataset has been discarded 20 water absorption bands from the original image, so there's 204
-		bands left in both of the tow dataset.
-		The Salinas Valley dataset has 16 different classes but the Salinas A only has 6 different classes.
-	\end{enumerate}
 	\begin{table}[h]
@@
 	\end{table}
+	In our experiment, we selected 4 real HSI dataset to train and test our DCCN model separately, that is, the
+	Pavia University(PU) dataset, the Pavia Center(PC) dataset, the Salinas Valley(SV) dataset and the Salinas A(SA)
+	dataset, which is a small subset of the Salinas Valley dataset.
+	The first three of them are relatively large dataset and the last one is relatively small.
+	We use these 4 dataset to test the robustness of out model when performing on different scale dataset.
+	Here follows the brief introduction of the four dataset(see table\ref{psgt}).
+	\begin{enumerate}[1)]
+		\item \textit{Pavia Center and University} These are two scenes acquired by the ROSIS sensor during a flight
+		campaign over Pavia, northern Italy.
+		The number of spectral bands is 102 for Pavia Centre and 103 for Pavia University.
+		Pavia Centre is a 1096×1096 pixels image, and Pavia University is 610×610 pixels, but some of the samples in
+		both images contain no information and have to be discarded before the analysis, so the final picture size is
+		1096×715 and 610×340.
+		The geometric resolution is 1.3 meters.
+		Both image has 9 different ground truth classes each.
+		\item \textit{Salinas Scene} The Salinas scene was collected by the 224-band AVIRIS sensor over Salinas Valley,
+		California, and is characterized by high spatial resolution (3.7-meter pixels).
+		The Salinas Valley dataset is a 512×217 pixels image, and the Salinas A is a subset of the Salinas Valley
+		containing 86×83 pixels.
+		The Salinas scene dataset has been discarded 20 water absorption bands from the original image, so there's 204
+		bands left in both of the tow dataset.
+		The Salinas Valley dataset has 16 different classes but the Salinas A only has 6 different classes.
+	\end{enumerate}
 
@@
 	From the results reported in table~\ref{result}, we can observe that our proposed DCCN model outperforms all the
-	other seven state-of-art models on all 4 dataset.
+	other seven state-of-the-art models on all 4 dataset.
 	Among all competitors in this experiment, 3D CNN\cite{hamida20183} and the CapsNet model performed relatively second
@@
 		\centering
+		\resizebox{\textwidth}{!}{
 			\begin{tabular}{|c|c|c|c|c|}
@@
 				\begin{tabular}{c}
-				\textbf{model}\\
+					\textbf{metrics}\\
 					\hline
 					{SVM}\\
-				{1D CNN\cite{hu2015deep}}\\
 					{2D CNN\cite{liu2017semi}}\\
 					{3D CNN\cite{hamida20183}}\\
+					{3D CNN-MS\cite{he2017multi}}\\
 					{3D FCN\cite{lee2016contextual}}\\
@@
 					{CapsNet}\\
-				{DCCN}\\
+					{DCCN}
 				\end{tabular}&
 				\begin{tabular}{ccc}
-				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
+					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
 					\hline
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
+					97.52±0.07 & 91.74±0.33 & 96.49±0.10\\
+					98.27±0.14 & 97.24±0.54 & 97.56±0.19\\
+					95.25±2.99 & 89.74±7.37 & 93.32±4.21\\
+					98.03±0.40 & 96.31±1.42 & 97.22±0.56\\
+					98.33±0.59 & 94.65±2.09 & 97.64±0.83\\
+					99.24±0.23 & 97.54±1.04 & 98.92±0.33\\
+					99.48±0.09 & 98.50±0.21 & 99.27±0.12\\
+					\textbf{99.53±0.02} & \textbf{98.59±0.20} & \textbf{99.34±0.03}
 				\end{tabular}&
 				\begin{tabular}{ccc}
-				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
+					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
 					\hline
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
+					79.86±0.26 & 64.26±0.45 & 71.86±0.39\\
+					93.74±0.42 & 95.61±0.79 & 91.85±0.54\\
+					77.92±12.22 & 85.34±7.42 & 73.42±13.63\\
+					93.39±1.34 & 95.97±1.39 & 91.42±1.72\\
+					88.45±1.66 & 85.58±3.22 & 84.49±2.22\\
+					98.07±0.62 & 96.80±1.06 & 97.44±0.82\\
+					97.69±0.60 & 96.82±0.83 & 96.94±0.80\\
+					\textbf{98.40±0.19} & \textbf{97.77±0.33} & \textbf{97.89±0.25}
 				\end{tabular}&
 				\begin{tabular}{ccc}
-				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
+					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
 					\hline
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
+					82.45±0.75 & 86.16±0.93 & 80.24±0.87\\
+					92.24±1.19 & 95.82±0.61 & 91.36±1.34\\
+					88.27±4.18 & 92.76±2.96 & 86.87±4.74\\
+					91.29±2.91 & 95.08±1.68 & 90.28±3.27\\
+					87.11±3.77 & 90.10±3.66 & 85.57±4.28\\
+					94.69±1.48 & 97.39±0.80 & 94.07±1.66\\
+					94.48±0.59 & 96.84±0.58 & 93.83±0.66\\
+					\textbf{95.00±0.59} & \textbf{97.30±0.50} & \textbf{94.42±0.66}
 				\end{tabular}&
 				\begin{tabular}{ccc}
-				\textbf{OA}&\textbf{AA}&\textbf{$\kappa$}\\
+					\textbf{AA(\%)}&\textbf{OA(\%)}&\textbf{$\kappa$(×100)}\\
 					\hline
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
-				100\%&100\%&100\%\\
+					97.44±0.19 & 97.42±0.22 & 96.80±0.23\\
+					84.47±0.51 & 89.86±0.69 & 81.22±0.62\\
+					79.27±4.74 & 80.81±8.80 & 74.70±5.96\\
+					79.92±4.91 & 85.46±5.01 & 75.99±5.69\\
+					86.54±3.72 & 85.55±4.30 & 83.09±4.65\\
+					98.00±1.61 & 97.10±2.33 & 97.48±2.03\\
+					99.52±0.10 & 99.31±0.15 & 99.40±0.13\\
+					\textbf{99.56±0.05} & \textbf{99.36±0.07} & \textbf{99.45±0.06}
 				\end{tabular}\\
@@
 			\end{tabular}
-		\caption{Final result of all adopted models.}
+		}
+		\caption{AA, OA and Kappa metrics for all 8 algorithms.
+		We can observe that out proposed model outperformed all competitor algorithms for all 4 dataset.}
 		\label{result}
@@
 
-	In figure~\ref{pupm,pcpm,svpm,sapm} we presented the classification maps outputted by our DCCN and seven competitor
+	In figure~\ref{pupm},\ref{pcpm},\ref{svpm},\ref{sapm} we presented the classification maps outputted by our DCCN and seven competitor
 	model after the training process.
@@
 		\end{subfigure}
+		\caption{Predicted map for all 8 algorithms on the Pavia Center dataset.}
 		\label{pcpm}
@@
 		\end{subfigure}
+		\caption{Predicted map for all 8 algorithms on the Pavia University dataset.}
 		\label{pupm}
@@
 		\end{subfigure}
+		\caption{Predicted map for all 8 algorithms on the Salinas Valley dataset.}
 		\label{svpm}
@@
 		\end{subfigure}
+		\caption{Predicted map for all 8 algorithms on the Salinas A dataset.}
 		\label{sapm}
@@
 	Finally, we presented the probability maps the eight algorithms produced of the four HSI dataset in
-	figure~\ref{pcpd ,pupd,svpd,sapd}.
+	figure~\ref{pcpd} ,\ref{pupd},\ref{svpd},\ref{sapd}.
 	\begin{figure}
@@
 		\end{subfigure}
+		\caption{Probability map for all 8 algorithms on the Pavia City dataset.}
 		\label{pcpd}
@@
 		\end{subfigure}
+		\caption{Probability map for all 8 algorithms on the Pavia City dataset.}
 		\label{pupd}
@@
 		\end{subfigure}
+		\caption{Probability map for all 8 algorithms on the Pavia City dataset.}
 		\label{svpd}
@@
 		\end{subfigure}
+		\caption{Probability map for all 8 algorithms on the Pavia City dataset.}
 		\label{sapd}

### 2020-03-13 calmetric.py

@@ -2,21 +2,18 @@ import argparse
 import numpy as np
 import re
 
-if __name__ == "__main__":
-	parser = argparse.ArgumentParser()
-	parser.add_argument("-d", "--directory")
-	args = parser.parse_args()
-	"./save/0312309/dccn/p7/pc/sum/sum.txt"
-	with open("./save/0312/liu/pc/data/sum.txt", "r") as f:
+
+def cal(path):
+	with open(path, "r") as f:
 		aa = []
 		oa = []
 		kappa = []
 		for line in f.readlines():
-			wordlist = re.split(", |:| ",line.strip())
+			wordlist = re.split(", |:", line.strip())
 			# print(wordlist)
-			oa.append((float)(wordlist[0]))
-			aa.append((float)(wordlist[1]))
-			kappa.append((float)(wordlist[2]))
+			oa.append((float)(wordlist[3]))
+			aa.append((float)(wordlist[5]))
+			kappa.append((float)(wordlist[7]))
 		# print(aa)
 		# print(oa)
 		# print(kappa)
@@ -27,11 +24,28 @@ if __name__ == "__main__":
 		aadiff = aamid - np.min(aa)
 		kpmid = (np.max(kappa) + np.min(kappa)) / 2
 		kpdiff = kpmid - np.min(kappa)
-		# oamid *=100
-		# oadiff *=100
-		aamid *=100
-		aadiff *=100
-		kpmid *=100
-		kpdiff *=100
+		oamid *= 100
+		oadiff *= 100
+		aamid *= 100
+		aadiff *= 100
+		kpmid *= 100
+		kpdiff *= 100
+		return oamid, aamid, kpmid
 
-		print("%.2f±%.2f & %.2f±%.2f & %.2f±%.2f\\\\" % (oamid, oadiff, aamid, aadiff, kpmid, kpdiff))
+
+if __name__ == "__main__":
+	parser = argparse.ArgumentParser()
+	parser.add_argument("-d", "--directory")
+	args = parser.parse_args()
+	oa = []
+	aa = []
+	kappa = []
+	for i in (1, 2, 3, 4, 5, 6, 7, 8, 9, 10):
+		path = "./save/03122/data/DCCN/r%02d/pu/sum/sum.txt" % i
+		rt = cal(path)
+		oa.append(rt[0])
+		aa.append(rt[1])
+		kappa.append(rt[2])
+	print(aa)
+	print(oa)
+	print(kappa)

### 2020-03-13 draw.py

@@ -1,0 +1,52 @@
+from dataloader import DataLoader
+from utils import selectData
+import numpy as np
+import pickle as pkl
+import seaborn as sns
+import matplotlib.pyplot as plt
+
+
+def load(path):
+	f = open(path, "rb")
+	return pkl.load(f)
+
+
+def convertToColor(map):
+	palette = {0: (0, 0, 0)}
+	for k, color in enumerate(sns.color_palette("hls", len(np.unique(map)))):
+		palette[k + 1] = tuple(np.asarray(255 * np.array(color), dtype='uint8'))
+	map = np.array(map, dtype=int)
+	unique = np.unique(map)
+	lut = np.zeros((int)(np.max(unique) + 1), dtype=np.int)
+	for it, i in enumerate(unique):
+		lut[i] = it
+	map = lut[map]
+	a = np.zeros(shape=(np.shape(map)[0], np.shape(map)[1], 3), dtype=np.uint8)
+	for i in range(np.shape(map)[0]):
+		for j in range(np.shape(map)[1]):
+			a[i][j] = palette[map[i][j]]
+	return a
+
+
+if __name__ == "__main__":
+	dpi = 100
+	dic = {"pc": 3, "pu": 2, "sl": 4, "sa": 5}
+	path = "./save/0312309/dccn/p7/sa/1/data/probmap.pkl"
+	map = load(path)
+	map = np.argmax(map, axis=1)
+	currentPx = 0
+	pathName, matName = selectData(5)
+	dataloader = DataLoader(pathName, matName, 7, 0.1, 1)
+	index = dataloader.loadAllLabeledData()[-1]
+	gt = np.zeros((dataloader.height, dataloader.width))
+	for i in range(len(map)):
+		idx = index[i]
+		h = idx // dataloader.width
+		w = idx % dataloader.width
+		gt[h][w] = map[i] + 1
+	plt.figure(figsize=(dataloader.width*5/dpi, dataloader.height*5/dpi))
+	plt.tick_params(axis='both', which='both', bottom=False, top=False, labelbottom=False, right=False, left=False,
+	                labelleft=False)
+	plt.imshow(convertToColor(gt))
+	# plt.subplots_adjust(left=0, bottom=0, right=1, top=1, wspace=0, hspace=0)
+	plt.show()

### 2020-03-13 postProcess.py

@@ -144,7 +144,7 @@ class ProbMap:
 		self.map = pickle.load(f)
 
 	def drawGt(self):
-		f=open("txt/wtf.txt", "w+")
+		# f=open("txt/wtf.txt", "w+")
 		plt.figure()
 		groundTruth = np.zeros(shape=(self.height, self.width),dtype=int)
 		# print(self.height,self.width,"8888888888")

### 2020-03-13 scripts/2020.sh

@@ -1,52 +1,52 @@
-python ./train.py -g 0 -e 100 --data 5 -l 0.0001 -p 7 -r 0.01 -m 1 -d ./save/03122/data/DCCN/r01/sa/ --model_path ./save/03122/model/DCCN/r01/sa/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/r01/sa/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 5 -l 0.0001 -p 7 -r 0.01 -m 1 -d ./save/03122/data/DCCN/r01/sa/ --model_path ./save/03122/model/DCCN/r01/sa/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/r01/sa/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 5 -l 0.0001 -p 7 -r 0.01 -m 1 -d ./save/03122/data/DCCN/r01/sa/ --model_path ./save/03122/model/DCCN/r01/sa/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/r01/sa/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 5 -l 0.0001 -p 7 -r 0.01 -m 1 -d ./save/03122/data/DCCN/r01/sa/ --model_path ./save/03122/model/DCCN/r01/sa/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/r01/sa/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 5 -l 0.0001 -p 7 -r 0.01 -m 1 -d ./save/03122/data/DCCN/r01/sa/ --model_path ./save/03122/model/DCCN/r01/sa/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/r01/sa/sum --dont_save_data
-python ./train.py -g 0 -e 100 --data 5 -l 0.0001 -p 7 -r 0.02 -m 1 -d ./save/03122/data/DCCN/r02/sa/ --model_path ./save/03122/model/DCCN/r02/sa/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/r02/sa/sum --dont_save_data
[…]

### 2020-03-13 scripts/2021.sh

@@ -1,51 +1,51 @@
-python ./train.py -g 1 -e 100 --data 5 -l 0.0001 -p 7 -r 0.01 -m 1 -d ./save/03122/data/DCCN/r01/sa/ --model_path ./save/03122/model/DCCN/r01/sa/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/r01/sa/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 5 -l 0.0001 -p 7 -r 0.01 -m 1 -d ./save/03122/data/DCCN/r01/sa/ --model_path ./save/03122/model/DCCN/r01/sa/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/r01/sa/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.01 -m 1 -d ./save/03122/data/DCCN/r01/pu/ --model_path ./save/03122/model/DCCN/r01/pu/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/r01/sa/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.01 -m 1 -d ./save/03122/data/DCCN/r01/pu/ --model_path ./save/03122/model/DCCN/r01/pu/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/r01/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.01 -m 1 -d ./save/03122/data/DCCN/r01/pu/ --model_path ./save/03122/model/DCCN/r01/pu/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/r01/pu/sum --dont_save_data
-python ./train.py -g 1 -e 100 --data 2 -l 0.0001 -p 7 -r 0.02 -m 1 -d ./save/03122/data/DCCN/r02/pu/ --model_path ./save/03122/model/DCCN/r02/pu/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/r02/pu/sum --dont_save_data
[…]

### 2020-03-13 scripts/2023.sh

@@ -1,23 +1,3 @@
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/03122/data/DCCN/p5/pu/ --model_path ./save/03122/model/DCCN/p5/pu/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/03122/data/DCCN/p5/pu/ --model_path ./save/03122/model/DCCN/p5/pu/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/03122/data/DCCN/p5/pu/ --model_path ./save/03122/model/DCCN/p5/pu/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/03122/data/DCCN/p5/pu/ --model_path ./save/03122/model/DCCN/p5/pu/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 5 -r 0.1 -m 1 -d ./save/03122/data/DCCN/p5/pu/ --model_path ./save/03122/model/DCCN/p5/pu/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/p5/pu/sum --dont_save_data
-python ./train.py -g 3 -e 100 --data 2 -l 0.0001 -p 7 -r 0.1 -m 1 -d ./save/03122/data/DCCN/p7/pu/ --model_path ./save/03122/model/DCCN/p7/pu/ --first_layer 8 --second_layer 16 --use_best_model --sum_path ./save/03122/data/DCCN/p7/pu/sum --dont_save_data
[…]

### 2020-03-13 draw.py
fixed some bugs

@@ -4,6 +4,7 @@ import numpy as np
 import pickle as pkl
 import seaborn as sns
 import matplotlib.pyplot as plt
+import argparse
 
 
 def load(path):
@@ -27,26 +28,34 @@ def convertToColor(map):
 			a[i][j] = palette[map[i][j]]
 	return a
 
+def draw(pic):
+	pass
+
 
 if __name__ == "__main__":
+	parser=argparse.ArgumentParser()
+	parser.add_argument("-d","--data",default="sa")
+	args=parser.parse_args()
 	dpi = 100
 	dic = {"pc": 3, "pu": 2, "sl": 4, "sa": 5}
-	path = "./save/0312309/dccn/p7/sa/1/data/probmap.pkl"
-	map = load(path)
-	map = np.argmax(map, axis=1)
-	currentPx = 0
-	pathName, matName = selectData(5)
-	dataloader = DataLoader(pathName, matName, 7, 0.1, 1)
-	index = dataloader.loadAllLabeledData()[-1]
-	gt = np.zeros((dataloader.height, dataloader.width))
-	for i in range(len(map)):
-		idx = index[i]
-		h = idx // dataloader.width
-		w = idx % dataloader.width
-		gt[h][w] = map[i] + 1
-	plt.figure(figsize=(dataloader.width*5/dpi, dataloader.height*5/dpi))
-	plt.tick_params(axis='both', which='both', bottom=False, top=False, labelbottom=False, right=False, left=False,
-	                labelleft=False)
-	plt.imshow(convertToColor(gt))
-	# plt.subplots_adjust(left=0, bottom=0, right=1, top=1, wspace=0, hspace=0)
-	plt.show()
+	for i in (args.data,):
+		path = "./save/0312309/data/DCCN/p7/"+i+"/1/data/probmap.pkl"
+		map = load(path)
+		map = np.argmax(map, axis=1)
+		currentPx = 0
+		pathName, matName = selectData(dic[i])
+		dl = DataLoader(pathName, matName, 7, 0.1, 1)
+		index = dl.loadAllLabeledData()[-1]
+		gt = np.zeros((dl.height, dl.width))
+		for i in range(len(map)):
+			idx = index[i]
+			h = idx // dl.width
+			w = idx % dl.width
+			gt[h][w] = map[i] + 1
+		plt.figure(figsize=(dl.width * 5 / dpi, dl.height * 5 / dpi))
[…]

### 2020-03-13 draw.py
draw dome

@@ -39,13 +39,16 @@ if __name__ == "__main__":
 	dpi = 100
 	dic = {"pc": 3, "pu": 2, "sl": 4, "sa": 5}
 	for i in (args.data,):
-		path = "./save/0312309/data/DCCN/p7/"+i+"/1/data/probmap.pkl"
-		map = load(path)
-		map = np.argmax(map, axis=1)
+		# path = "./save/0312309/data/DCCN/p7/"+i+"/1/data/probmap.pkl"
+		path="./save/0312309/dccn/p7/sa/1/data/probmap.pkl"
+		pmap = load(path)
+		map = np.argmax(pmap, axis=1)
 		currentPx = 0
 		pathName, matName = selectData(dic[i])
 		dl = DataLoader(pathName, matName, 7, 0.1, 1)
 		index = dl.loadAllLabeledData()[-1]
+		grdt=dl.label
+		print(np.max(grdt))
 		gt = np.zeros((dl.height, dl.width))
 		for i in range(len(map)):
 			idx = index[i]
@@ -56,6 +59,16 @@ if __name__ == "__main__":
 		plt.tick_params(axis='both', which='both', bottom=False, top=False, labelbottom=False, right=False, left=False,
 						labelleft=False)
 		plt.imshow(convertToColor(gt))
-		# plt.subplots_adjust(left=0, bottom=0, right=1, top=1, wspace=0, hspace=0)
+		pm=np.zeros((dl.height,dl.width))
+		for i in range(len(map)):
+			idx=index[i]
+			h = idx // dl.width
+			w = idx % dl.width
+			# print(h,w)
+			pm[h][w]=pmap[i][grdt[h][w]-1]
+		plt.figure(figsize=(dl.width * 5 / dpi, dl.height * 5 / dpi))
+		plt.tick_params(axis='both', which='both', bottom=False, top=False, labelbottom=False, right=False, left=False,
+		                labelleft=False)
+		plt.imshow(pm)
 		plt.show()
 		del(dl)

### 2020-03-13 draw.py
fixed some bugs

@@ -5,6 +5,7 @@ import pickle as pkl
 import seaborn as sns
 import matplotlib.pyplot as plt
 import argparse
+import os
 
 
 def load(path):
@@ -38,9 +39,13 @@ if __name__ == "__main__":
 	args=parser.parse_args()
 	dpi = 100
 	dic = {"pc": 3, "pu": 2, "sl": 4, "sa": 5}
+	if not os.path.exists("save/0313/img/dccn/"):
+		os.makedirs("save/0313/img/dccn/")
 	for i in (args.data,):
-		# path = "./save/0312309/data/DCCN/p7/"+i+"/1/data/probmap.pkl"
-		path="./save/0312309/dccn/p7/sa/1/data/probmap.pkl"
+		path = "./save/0312309/data/DCCN/p7/"+i+"/1/data/probmap.pkl"
+		spd="save/0313/img/dccn/"+i+"pdm.eps"
+		spb = "save/0313/img/dccn/" + i + "pbm.eps"
+		# path="./save/0312309/dccn/p7/sa/1/data/probmap.pkl"
 		pmap = load(path)
 		map = np.argmax(pmap, axis=1)
 		currentPx = 0
@@ -59,6 +64,8 @@ if __name__ == "__main__":
 		plt.tick_params(axis='both', which='both', bottom=False, top=False, labelbottom=False, right=False, left=False,
 						labelleft=False)
 		plt.imshow(convertToColor(gt))
+		sv = plt.gcf()
+		sv.savefig(spd, format="eps", dpi=dpi)
 		pm=np.zeros((dl.height,dl.width))
 		for i in range(len(map)):
 			idx=index[i]
@@ -70,5 +77,5 @@ if __name__ == "__main__":
 		plt.tick_params(axis='both', which='both', bottom=False, top=False, labelbottom=False, right=False, left=False,
 		                labelleft=False)
 		plt.imshow(pm)
-		plt.show()
-		del(dl)
+		sv = plt.gcf()
+		sv.savefig(spb, format="eps", dpi=dpi)
